\documentclass[conference]{IEEEtran}

% ─── Packages ─────────────────────────────────────────────────────────────────
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{float}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{array}
\usepackage{listings}
\usepackage{cite}

\pgfplotsset{compat=1.18}
\usepgfplotslibrary{groupplots}
\usetikzlibrary{patterns}

% ─── Colors ───────────────────────────────────────────────────────────────────
\definecolor{rdmacolor}{HTML}{E74C3C}
\definecolor{numacolor}{HTML}{2E86C1}
\definecolor{papercolor}{HTML}{27AE60}
\definecolor{codebg}{HTML}{F5F5F5}
\definecolor{codeframe}{HTML}{CCCCCC}

% ─── Listings ─────────────────────────────────────────────────────────────────
\lstset{
  basicstyle=\ttfamily\small,
  backgroundcolor=\color{codebg},
  frame=single,
  rulecolor=\color{codeframe},
  breaklines=true,
  columns=fullflexible
}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black
}

% ─── Title ────────────────────────────────────────────────────────────────────
\title{Outback RDMA Key-Value Store:\\
Reproduction, CXL Extension, and Comparative Analysis}
\author{\IEEEauthorblockN{Cheng-Shun Chuang}\\
\small Source code: \url{https://github.com/Ulrixon/outback-cxl-numa}}

\begin{document}
\maketitle

% ══════════════════════════════════════════════════════════════════════════════
\section{Introduction}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{Background}

Outback~\cite{outback} is an RDMA-based Key-Value Store designed for disaggregated memory architectures. It employs a disaggregated memory model where Memory Nodes (MN) store KV data and Compute Nodes (CN) maintain a lightweight Dynamic Minimal Perfect Hashing (DMPH) index locally. The DMPH index (composed of Ludo~\cite{ludo} seed arrays and an Othello bucket locator) enables clients to resolve key locations with a single one-sided RDMA read, avoiding the CPU overhead of two-sided RPC on the memory node. The original paper claims up to a 5.03$\times$ throughput gain over baselines (RACE~\cite{race}, RPC-MICA~\cite{mica}) and a minimal memory footprint (12.5\,MB to index 20M KV pairs). When the hash table exceeds its load factor threshold, a resize operation rebuilds the DMPH index and redistributes data.

Compute Express Link (CXL)~\cite{cxl} is an open interconnect standard built on PCIe that enables cache-coherent shared memory between host CPUs and attached devices. CXL.mem provides load/store semantics to remote memory at sub-microsecond latency ($\sim$150--300\,ns), significantly faster than RDMA ($\sim$2--5\,$\mu$s) but slower than local DRAM ($\sim$100\,ns).

\subsection{Project Goal}

This project has two objectives:
\begin{enumerate}[nosep]
  \item \textbf{Reproduction:} Reproduce the original Outback RDMA experiments on CloudLab Apt \texttt{r320} nodes using the same Mellanox MX354A ConnectX-3 InfiniBand FDR (56\,Gbps) hardware as the paper's Figure~10 cluster, and analyze discrepancies against the paper's published results (Figures~9--17).
  \item \textbf{Extension:} Port Outback to a CXL-based platform by emulating CXL memory disaggregation through NUMA inter-socket shared memory on a CloudLab c6420 node, and compare the results against both the paper and the RDMA reproduction.
\end{enumerate}

Since dedicated CXL hardware was unavailable, we emulated CXL memory disaggregation using \textbf{NUMA inter-socket memory}. On a dual-socket machine, one NUMA node's memory serves as the ``remote'' Memory Node, while CPUs on the other socket act as Compute Nodes accessing that memory across the inter-socket UPI interconnect. This provides load/store semantics with $\sim$100--200\,ns cross-socket latency --- a useful functional proxy for CXL.mem because it provides load/store access to remote memory. However, it is not a performance-equivalent substitute for real CXL hardware: NUMA avoids PCIe/CXL controller overhead and uses local server DRAM bandwidth, so the CXL/NUMA results should be interpreted as an \textbf{optimistic upper bound} on what a real CXL-based Outback design might achieve.

% ══════════════════════════════════════════════════════════════════════════════
\section{Literature Review}\label{sec:litreview}
% ══════════════════════════════════════════════════════════════════════════════

\subsection*{The Reproduced Paper: Outback}

\textbf{Outback}~\cite{outback} addresses the \emph{one-sided vs.\ two-sided RDMA dilemma}: one-sided RDMA requires multiple round trips for traditional hash or tree indexes; two-sided RPC resolves the index in one round trip but imposes CPU load on memory nodes. Outback resolves this by splitting the index into (1)~a \emph{compute-heavy, memory-efficient} DMPH seed component (Ludo~\cite{ludo} arrays) cached on compute nodes, and (2)~a \emph{memory-heavy, compute-efficient} Othello bucket-locator on memory nodes accessed with a single one-sided RDMA READ. Evaluated on Mellanox CX-6 100\,Gbps IB, it achieves 1.06--5.03$\times$ over baselines on YCSB. Published in \emph{PVLDB}, vol.\ 18, 2024.

\subsection*{Baseline Systems}

\textbf{RACE}~\cite{race} (\emph{USENIX ATC 2021}) is an extendible hashing index for disaggregated memory using only one-sided RDMA verbs. Outback reports 2.43--5.03$\times$ over RACE on YCSB-A/C. \textbf{MICA}~\cite{mica} (\emph{USENIX NSDI 2014}) is a single-machine KV store with kernel-bypass networking, invoked via two-sided RPC (\textit{RPC-MICA}) in Outback's evaluation (2.47\,MOPS, YCSB-C). \textbf{Cluster RPC} (similar to DrTM+R~\cite{drtmr}) reaches $\sim$5.41\,MOPS at 72 threads via two-sided RPC. \textbf{FaSST}~\cite{fasst} (\emph{OSDI 2016}), \textbf{DrTM+R}~\cite{drtmr} (\emph{OSDI 2018}), and \textbf{ROLEX}~\cite{rolex} (\emph{USENIX FAST 2023}) are included in the codebase but have build-breaking issues that prevented comparison (\S\ref{sec:codebase-issues}).

\subsection*{Key Primitives and CXL Context}

\textbf{Ludo Hashing}~\cite{ludo} (\emph{ACM SIGMETRICS 2020}) achieves $3.76 + 1.05\ell$ bits per KV item (near the information-theoretic minimum) with dynamic insertions; it forms Outback's DMPH seed arrays. \textbf{YCSB}~\cite{ycsb} (\emph{ACM SoCC 2010}) provides workloads A--F (read-heavy to write-heavy); the main steady-state YCSB experiments use 50\,M KV pairs and a 10\,M-key working set unless otherwise stated (resize experiments use 20\,M keys; stress tests vary key count). \textbf{CXL}~\cite{cxl} is an open PCIe-based interconnect providing cache-coherent load/store remote memory at 150--300\,ns; CXL~3.0 supports multi-node pooling. In this work, CXL.mem is emulated via NUMA inter-socket shared memory (UPI $\sim$100--200\,ns).

% ══════════════════════════════════════════════════════════════════════════════
\section{Environment Setup}
% ══════════════════════════════════════════════════════════════════════════════

Five hardware configurations are compared throughout this report: the paper's \texttt{r650} CX-6 cluster, the paper's \texttt{r320} CX-3 cluster, our 3-node \texttt{r320} RDMA reproduction (same-rack), our 9-node \texttt{r320} RDMA reproduction (multi-rack), and our \texttt{c6420} NUMA-based CXL proxy. Table~\ref{tab:setup-diff} lists the key differences; full hardware listings appear in Appendix~\ref{app:hw}.

\begin{table*}[!t]
\centering
\caption{Setup comparison across all five hardware environments. The 9-node matches paper Fig.~10's exact topology; the key differentiator from 3-node is multi-rack RTT ($\sim$29\,$\mu$s vs.\ $\sim$2\,$\mu$s), which makes the client the throughput bottleneck at coro=2. Peak throughput values are YCSB-C maxima.}
\label{tab:setup-diff}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}llllll@{}}
\toprule
\textbf{Factor} & \textbf{Paper (r650, Fig.~9)} & \textbf{Paper (r320, Fig.~10)} & \textbf{3-node (ours)} & \textbf{9-node (ours)} & \textbf{CXL (c6420)} \\
\midrule
NIC Speed & CX-6, 100\,Gbps IB & CX-3 MX354A, 56\,Gbps FDR & CX-3 MX354A, 56\,Gbps FDR & CX-3 MX354A, 56\,Gbps FDR & N/A (load/store) \\
CPU & Xeon Platinum 8360Y & Xeon E5-2450, 8C & Xeon E5-2450, 8C & Xeon E5-2450, 8C & 2$\times$Xeon Gold 6142 \\
Max Threads & 144/shard & 64 (8\,CN$\times$8T) & 32 (2\,CN$\times$16T) & 64 (8\,CN$\times$8T) & 32 (1 socket) \\
MN Threads & 1--3 (2 shards) & 4 & 1--3 & 1--4 & none (no MN CPU)$^a$ \\
Node Count & 6 (2 shards$\times$3) & 9 (1\,MN+8\,CN) & 3 (1\,MN+2\,CN) & 9 (1\,MN+8\,CN) & 1 \\
Memory & 256\,GB & 16\,GB DDR3 & 16\,GB DDR3 & 16\,GB DDR3 & 384\,GB DDR4 \\
Interconnect & IB FDR $\sim$1\,$\mu$s & IB FDR, multi-rack & IB FDR, same-rack & IB FDR, multi-rack & UPI $\sim$150\,ns \\
RTT (meas.) & $\sim$1\,$\mu$s & $\sim$29\,$\mu$s & $\sim$2\,$\mu$s & $\sim$29\,$\mu$s & $\sim$0.15\,$\mu$s \\
Peak Tput & 6.0\,MOPS & 17.0\,MOPS (4\,MT) & 5.04\,MOPS & 4.75\,MOPS & 118\,MOPS \\
\bottomrule
\end{tabular}}
\vspace{2pt}
{\scriptsize $^a$In CXL/NUMA the ``memory node'' is NUMA node~1's DRAM only --- no MN CPU runs. Compute threads on NUMA0 access data via direct \texttt{load}/\texttt{store} over UPI. The \texttt{mem\_threads} parameter is repurposed as \textbf{insert-lane sharding} (partitions the allocation counter to reduce CAS contention); it has no effect on the read path and only limited effect on write-heavy workloads because contention remains beyond the allocation counter. Measured throughput varies by $<$2\% across 1--3 \texttt{mem\_threads} (\S\ref{sec:repro-mt}).}
\end{table*}

\textbf{Network bandwidth (56 vs.\ 100\,Gbps).} Our RDMA nodes use CX-3 FDR InfiniBand at 56\,Gbps while the paper's primary cluster uses CX-6 at 100\,Gbps. This $\sim$2$\times$ bandwidth gap caps our per-MN aggregate throughput. Because our hardware is identical to the paper's Figure~10 cluster (\texttt{r320}, CX-3 FDR), per-MN-thread comparisons against Fig.~10 are like-for-like; comparisons against Fig.~9 (CX-6) are expected to be proportionally lower.

\textbf{Cluster scale and thread count (3 vs.\ 9 nodes).} We allocated 3 \texttt{r320} nodes (1\,MN + 2\,CN) versus the paper's maximum of 9. Total client-side parallelism is capped at 32 threads, preventing testing of the 64--144 thread regime in the paper's scaling curves.

\textbf{Memory per node (16\,GB vs.\ 256\,GB).} The \texttt{r320}'s 16\,GB DDR3 causes OOM at 80\,M keys once the raw KV array, DMPH index, and pre-registered hugepage MR are all resident simultaneously. Unless otherwise noted, all RDMA experiments use 50\,M keys. Resize experiments use 20\,M keys to match the paper's Figure~17 setup, while stress tests intentionally vary the key count to expose memory limits. The CXL \texttt{c6420} node's 384\,GB accommodates 80\,M with headroom.

\textbf{Interconnect latency (InfiniBand vs.\ NUMA/UPI).} RDMA over InfiniBand incurs $\sim$2--5\,$\mu$s per round trip. The CXL/NUMA path uses Intel UPI inter-socket load/store at $\sim$100--200\,ns --- roughly 20$\times$ lower latency --- eliminating the serialization bottleneck on the memory-node CPU and enabling the near-linear throughput scaling seen in \S\ref{sec:cxl-results}.

\textbf{CXL is emulated, not real hardware.} Real CXL.mem devices (e.g., Samsung CMM-D) exhibit 200--400\,ns latency and are constrained by PCIe bandwidth ($\sim$32\,GB/s for PCIe~5.0 $\times$16). Our NUMA emulation at $\sim$150\,ns with DDR4 bandwidth is an optimistic upper bound; see \S\ref{sec:conclusion-limitations} for implications.

% ══════════════════════════════════════════════════════════════════════════════
\section{Findings: Build Effort and Issues}
% ══════════════════════════════════════════════════════════════════════════════

This section documents the practical challenges encountered in setting up and running the experiments. These issues are not discussed in the original paper but significantly affect reproducibility.

\subsection{RDMA Setup Challenges}

Getting Outback's RDMA code running required resolving several compatibility issues not documented by the paper:

\begin{itemize}[nosep]
  \item \textbf{OFED driver:} Default Ubuntu 20.04 OFED was incompatible with CX-3. Required downgrade to MLNX\_OFED~4.9-x (the last release supporting CX-3), including manual removal of the pre-installed driver stack and OFED reinstall via \texttt{mlnxofedinstall}.
  \item \textbf{Kernel version:} Ubuntu~22.04 (kernel~5.15) failed to compile the R2 \texttt{xcomm} transport layer due to deprecated \texttt{ib\_*} APIs; Ubuntu~20.04 (kernel~5.4) was required.
  \item \textbf{NIC port index:} Source hardcodes the NIC port; on several nodes only port~1 (not port~0) was connected, requiring manual correction via \texttt{ibv\_devinfo} and a code edit.
  \item \textbf{Hardware availability:} Only nodes carrying legacy ConnectX-3 (\texttt{mlx4}) hardware work with the artifact; securing 3 simultaneous CX-3 nodes on CloudLab required scheduling around availability windows.
  \item \textbf{Build dependencies:} Requires cmake~$\geq$3.16, boost~1.65+, gflags, and MICA-specific Mellanox headers not covered by \texttt{setup-env.sh}.
\end{itemize}

\subsection{CXL/NUMA Implementation Effort}

Porting Outback from RDMA to CXL/NUMA required \textbf{fundamental architectural changes} across six subsystems. Table~\ref{tab:impl-comparison} summarizes the scope.

\begin{table}[H]
\centering
\caption{Architectural changes: RDMA $\to$ CXL/NUMA}
\label{tab:impl-comparison}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}p{1.8cm}p{4.5cm}p{5.0cm}@{}}
\toprule
\textbf{Component} & \textbf{RDMA (Original)} & \textbf{CXL/NUMA (This Work)} \\
\midrule
Transport &
  Mellanox NIC, \texttt{UDTransport}, hardware MRs, RPC polling loop &
  POSIX shared memory (\texttt{shm\_open}/\texttt{mmap}), \texttt{numa\_alloc\_onnode()} binds pages to socket \\
\addlinespace
Execution Model &
  R2 coroutine scheduler; async yields (\texttt{R2\_ASYNC\_WAIT}) hide RDMA RTT &
  Direct pointer dereference; \texttt{-{}-coros} repurposed as inner-loop batch factor \\
\addlinespace
Concurrency &
  Hardware Queue Pairs on NIC multiplex traffic &
  Software allocation lanes: \texttt{lane\_next\_free\_index[N]} with \texttt{thread\_id \% N} \\
\addlinespace
Telemetry &
  Running-total averages per second &
  Lock-free 2D histogram; P95/P99/P999 from bucket parse at teardown \\
\addlinespace
Lifecycle &
  Kernel cleans sockets on exit &
  \texttt{sigaction(SIGINT/SIGTERM)} $\to$ \texttt{cleanup\_numa\_ipc()}: msync/munmap/shm\_unlink \\
\addlinespace
Resize &
  Separate branch; limited scenarios &
  6-state machine (see \S\ref{sec:resize-sm}); versioned epochs \\
\bottomrule
\end{tabular}}
\end{table}

\subsubsection{Transport Layer: RDMA $\to$ POSIX Shared Memory}
The RDMA server registers memory regions via Mellanox NIC and serves them through Queue Pairs using \texttt{UDTransport}. In the NUMA port, \texttt{shm\_open()} creates files in \texttt{/dev/shm/}, \texttt{ftruncate()} sizes them, and \texttt{numa\_alloc\_onnode()} binds pages to NUMA node~1. A \texttt{SharedNumaRegistry} metadata structure stores server state, resize epochs, client liveness, and allocation lanes. Clients call \texttt{mmap()} to map the server's memory directly --- emulating CXL.mem load/store semantics.

\subsubsection{Execution Model: Coroutines $\to$ Synchronous Batched Loops}
RDMA's $\sim$2--5\,$\mu$s round-trip justified the R2 coroutine scheduler. With NUMA cross-socket latency at $\sim$100--200\,ns, coroutine context-switching ($\sim$50--100\,ns) would exceed the access time. All coroutine logic was removed; \texttt{numa\_search()} executes as a direct pointer dereference.

\subsubsection{Concurrency: Queue Pairs $\to$ Software Lanes}
Without NIC hardware, concurrent \texttt{\_\_sync\_fetch\_and\_add} operations cause cache-line bouncing. Setting \texttt{-{}-mem\_threads=N} creates $N$ independent atomic counters; each thread selects its lane via \texttt{thread\_id \% N}.

\subsubsection{Resize State Machine}\label{sec:resize-sm}
A six-state orchestrator was implemented:
\begin{center}
\small
$\text{NORMAL} \to \text{PRE\_RESIZE} \to \text{COPYING}$ \\
$\to \text{READY\_TO\_SWITCH} \to \text{DRAIN\_OLD} \to \text{GC\_PENDING} \to \text{NORMAL}$
\end{center}
Each epoch creates a new versioned shared-memory region. Clients detect changes through a generation counter and transparently remap. Structural mutations are deferred during COPYING/DRAIN and replayed after the switch.

\subsection{Codebase Issues Discovered}\label{sec:codebase-issues}

During reproduction, we discovered several undisclosed codebase limitations:

\begin{itemize}[nosep]
  \item \textbf{Resize on separate branch:} The resizing code was found on a separate Git branch with hard-coded 30-second benchmark limits. The standard main-branch tests run \textbf{without resizing enabled}, drastically altering the performance profile compared to the paper's Figure~17.
  \item \textbf{Broken zipfian for datasets:} Zipfian distribution for FB/OSM datasets was non-functional in the source code, despite the paper showing zipfian results (Figure~11c,d). The code accepts zipfian parameters but only applies them to YCSB workloads.
  \item \textbf{Memory requirements undisclosed:} 80M KV pairs causes an OOM on the r320's 16\,GB DRAM (the raw KV array plus the DMPH index plus the pre-registered RDMA huge-page MR exceed available memory), while the paper tests 80M on r650 (256\,GB) without disclosing this footprint.
  \item \textbf{No DMPH memory monitor:} The source lacked any way to measure the DMPH index size that the paper prominently reports in Figure~16. We developed a custom monitor from scratch.
  \item \textbf{Narrow hardware compatibility:} The paper does not disclose the strict driver/kernel/NIC requirements described in \S3.1.
  \item \textbf{YCSB-E (range scan) unimplemented:} We attempted to evaluate YCSB-E (95\% Scan, 5\% Insert), which tests range query performance --- a critical workload for real applications. The original source code does not implement range scan operations at all, and the paper does not report YCSB-E results. This is a significant omission: DMPH-based indexing provides $O(1)$ point lookups but has no inherent support for ordered iteration, making range scans fundamentally difficult for Outback's architecture.
\end{itemize}

% ══════════════════════════════════════════════════════════════════════════════
\section{Reproduction Results: RDMA vs.\ Original Paper}
% ══════════════════════════════════════════════════════════════════════════════

This section systematically compares our RDMA reproduction against each of the paper's published figures (Figures~9--17). For each figure, we present the paper's reported values alongside our measurements and analyze any discrepancies.

\subsection{YCSB Throughput (Paper Figures~9--10)}\label{sec:repro-ycsb}

All RDMA experiments use the default configuration: 50\,M keys (unless otherwise noted --- see \S\ref{sec:repro-resize} for the 20\,M resize experiment and \S\ref{sec:stress} for stress tests), DMPH load factor = 0.95, coroutine = 2, mem\_threads = 1, 120\,s duration. Our CX-3 nodes have only 8 physical cores (16 HT threads) per node, so the maximum properly-assigned thread count is 16 per CN, or 32 across 2\,CN.

\subsubsection{Individual YCSB Workload Results}

Per-thread throughput and latency measurements for all five YCSB workloads (C, B, A, D, F) at both 1CN and 2CN configurations are presented in Tables~\ref{tab:rdma-ycsbc}--\ref{tab:rdma-ycsbf} (Appendix~\ref{app:tables}). Key observations: read-dominated workloads (C, B, D) saturate at 4.3--5.0\,MOPS at 32 threads (2CN), while write-heavy YCSB-F peaks at only 2.5\,MOPS (16T, 2CN) and degrades at 32T due to insert/update contention. All workloads exhibit a ``hockey stick'' latency curve: flat at $\sim$2\,$\mu$s through saturation, then steeply rising.

\subsubsection{RDMA vs.\ Paper YCSB Comparison}

\begin{figure*}[t]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=0.92\textwidth,
    height=8.5cm,
    ylabel={Throughput (MOPS)},
    xlabel={Number of CN Threads},
    xmode=log, log basis x=2,
    xtick={1,2,4,8,16,32,64,144},
    xticklabels={1,2,4,8,16,32,64,144},
    x tick label style={rotate=30,anchor=east,font=\tiny},
    xmin=1, xmax=200,
    ymin=0, ymax=20,
    legend style={at={(0.02,0.98)},anchor=north west,font=\scriptsize,
            fill=white,fill opacity=1,draw=black!30,text opacity=1},
    every axis plot/.append style={mark size=2.5pt, thick},
    grid=major, grid style={gray!30},
]
% Our RDMA reproduction (1CN): filled markers
\addplot[color=numacolor,mark=square*]
  coordinates {(1,0.724)(2,1.411)(4,2.770)(8,4.503)(16,4.325)};
\addplot[color=teal,mark=triangle*]
  coordinates {(1,0.731)(2,1.451)(4,2.836)(8,3.722)(16,4.091)};
\addplot[color=orange,mark=diamond*]
  coordinates {(1,0.740)(2,1.471)(4,2.746)(8,3.632)(16,3.783)};
\addplot[color=purple!80,mark=pentagon*]
  coordinates {(1,0.744)(2,1.460)(4,2.699)(8,3.832)(16,3.900)};
\addplot[color=rdmacolor,mark=star]
  coordinates {(1,0.626)(2,1.194)(4,1.939)(8,2.213)(16,2.370)};
% Our RDMA reproduction (2CN): hollow markers, same colors/shapes as 1CN
\addplot[color=numacolor,mark=square*,mark options={fill=white}]
  coordinates {(4,2.802)(8,4.269)(16,4.833)(32,5.040)};
\addplot[color=teal,mark=triangle*,mark options={fill=white}]
  coordinates {(4,2.777)(8,4.043)(16,4.461)(32,4.439)};
\addplot[color=orange,mark=diamond*,mark options={fill=white}]
  coordinates {(4,2.709)(8,3.649)(16,3.873)(32,4.049)};
\addplot[color=purple!80,mark=pentagon*,mark options={fill=white}]
  coordinates {(4,2.720)(8,3.982)(16,4.229)(32,4.281)};
\addplot[color=rdmacolor,mark=star,mark options={fill=white}]
  coordinates {(4,1.926)(8,2.157)(16,2.501)(32,2.354)};
% Our 9-node (1MN+8CN, MT=1, coro=2): × markers, same workload colors
\addplot[color=numacolor,mark=x,mark options={scale=1.6,line width=0.8pt}]
  coordinates {(8,2.447)(16,3.397)(32,4.361)(64,4.655)};
\addplot[color=teal,mark=x,mark options={scale=1.6,line width=0.8pt}]
  coordinates {(8,2.475)(16,3.236)(32,3.769)(64,3.914)};
\addplot[color=orange,mark=x,mark options={scale=1.6,line width=0.8pt}]
  coordinates {(8,2.763)(16,3.111)(32,3.454)(64,3.783)};
\addplot[color=purple!80,mark=x,mark options={scale=1.6,line width=0.8pt}]
  coordinates {(8,3.043)(16,3.595)(32,3.690)(64,4.073)};
\addplot[color=rdmacolor,mark=x,mark options={scale=1.6,line width=0.8pt}]
  coordinates {(8,2.114)(16,2.274)(32,2.379)(64,2.530)};
% Paper Fig.~9 Outback curves (CX-6, 1 MN thread, up to 144T) -- dashed, no markers
\addplot[color=numacolor,mark=none,densely dashed,thick]
  coordinates {(8,1.0)(12,2.0)(20,3.5)(72,5.7)(108,6.0)(144,6.01)};
\addplot[color=teal,mark=none,densely dashed,thick]
  coordinates {(8,3.5)(12,4.2)(20,4.9)(72,5.8)(108,5.9)(144,6.0)};
\addplot[color=orange,mark=none,densely dashed,thick]
  coordinates {(8,3.8)(12,4.5)(20,5.0)(72,5.2)(108,5.3)(144,5.5)};
\addplot[color=purple!80,mark=none,densely dashed,thick]
  coordinates {(8,3.8)(12,4.5)(20,5.0)(72,5.2)(108,5.3)(144,5.5)};
\addplot[color=rdmacolor,mark=none,densely dashed,thick]
  coordinates {(8,1.3)(12,2.1)(20,2.8)(72,3.2)(108,3.4)(144,3.62)};
% Paper Fig.~10 Outback curves (CX-3, 4 MN threads, up to 64T) -- dotted, no markers
\addplot[color=numacolor,mark=none,dotted,thick]
  coordinates {(8,9.0)(16,12.5)(24,14.5)(32,15.5)(48,17.0)(64,17.0)};
\addplot[color=teal,mark=none,dotted,thick]
  coordinates {(8,10.0)(16,13.0)(24,14.5)(32,15.5)(48,16.0)(64,16.5)};
\addplot[color=orange,mark=none,dotted,thick]
  coordinates {(8,8.0)(16,11.0)(24,13.0)(32,14.0)(48,15.0)(64,15.0)};
\addplot[color=purple!80,mark=none,dotted,thick]
  coordinates {(8,9.0)(16,11.5)(24,13.0)(32,14.5)(48,15.5)(64,16.0)};
\addplot[color=rdmacolor,mark=none,dotted,thick]
  coordinates {(8,5.0)(16,7.0)(24,8.0)(32,8.5)(48,9.0)(64,9.0)};
\legend{C, B, A, D, F}
\end{axis}
\end{tikzpicture}
\vspace{2pt}
\parbox{0.92\textwidth}{\centering\scriptsize
Filled markers: ours 1CN (1--16T) \quad Hollow markers: ours 2CN (4--32T) \quad $\times$ markers: ours 9-node (1MN+8CN, 8--64T, MT=1) \\
Dashed lines: Fig.~9 (6$\times$r650, CX-6, 1\,MNT/shard) \quad Dotted lines: Fig.~10 (9$\times$r320, CX-3, 4\,MNT)
}
\caption{Four-way RDMA comparison across setups. \textbf{Solid filled markers} = our r320 reproduction with 1\,CN (1\,MN+1\,CN, coro=2, 1--16\,T). \textbf{Solid hollow markers} = our r320 reproduction with 2\,CN (1\,MN+2\,CN, coro=2, 4--32\,T). \textbf{$\times$ markers} = our 9-node cluster (1\,MN+8\,CN, MT=1, coro=2, 8--64\,T). All three use the same CX-3 MX354A IB FDR 56\,Gbps hardware. \textbf{Dashed lines} = paper Fig.~9 Outback (6$\times$r650, CX-6 100\,Gbps, 1\,MN+2\,CN per shard, 1\,MNT/shard, up to 144\,T/shard). \textbf{Dotted lines} = paper Fig.~10 Outback (9$\times$r320, CX-3 56\,Gbps, 1\,MN+8\,CN, 4\,MN threads, up to 64\,T). Same color per workload across all sources. The 9-node ($\times$) curves plateau at 3.9--4.7\,MOPS and fail to reach the 2CN hollow-marker peaks despite $2\times$ the CN threads --- a direct consequence of multi-rack RTT ($\sim$29\,$\mu$s) and a throughput ceiling that additional coroutines (C=1--3) do not lift. The paper's dotted CX-3 curves (same hardware, same topology) reach 17\,MOPS at 4\,MN threads; this gap is not fully explained by our experiments and likely reflects undisclosed benchmark configuration differences.}
\label{fig:rdma-ycsb-all}
\end{figure*}

\begin{figure}[H]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6cm,
    ylabel={Throughput (MOPS)},
    xlabel={Workload},
    symbolic x coords={YCSB-C,YCSB-B,YCSB-A,YCSB-D,YCSB-F},
    xtick=data,
    ymin=0, ymax=7,
    bar width=7pt,
    legend style={at={(0.5,-0.28)},anchor=north,font=\small,legend columns=3},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=45,anchor=south west},
    title={RDMA Peak Throughput: 3-node vs.\ 9-node vs.\ Paper}
]
\addplot[fill=rdmacolor!80] coordinates {
  (YCSB-C,5.040)(YCSB-B,4.439)(YCSB-A,4.049)(YCSB-D,4.281)(YCSB-F,2.354)
};
\addplot[fill=orange!70] coordinates {
  (YCSB-C,4.752)(YCSB-B,4.181)(YCSB-A,3.783)(YCSB-D,4.073)(YCSB-F,2.530)
};
\addplot[fill=papercolor!80] coordinates {
  (YCSB-C,6.01)(YCSB-B,5.82)(YCSB-A,5.50)(YCSB-D,5.90)(YCSB-F,3.62)
};
\legend{3-node (CX-3{,} 32T), 9-node (CX-3{,} 64T), Paper (CX-6{,} 144T)}
\end{axis}
\end{tikzpicture}}%
\caption{RDMA peak throughput per workload across three setups. Our 3-node (32T, 1MN+2CN) and 9-node (64T, 1MN+8CN) both use identical CX-3 r320 hardware; despite $2\times$ the CN threads, the 9-node is slightly below the 3-node peak --- multi-rack RTT ($\sim$29\,$\mu$s) limits throughput regardless of CN count. Both are below the paper's CX-6 peaks ($6\times$r650, 144T).}
\label{fig:rdma-ycsb-peaks}
\end{figure}

\subsubsection{Comparison to Paper Figure~9}

The paper's Figure~9 reports throughput on r650 nodes with CX-6 100\,Gbps NICs using 6 nodes (2 shards of 1\,MN + 2\,CN each) and up to 144 CN threads. Our RDMA reproduction reaches 65--84\% of the paper's CX-6 peaks even though our NIC is roughly half the link bandwidth (56\,Gbps FDR vs.\ 100\,Gbps CX-6) and we have only one quarter the CN count. Per-MN-thread throughput is comparable: the paper's single MN thread serves $\sim$6\,MOPS on CX-6; our single MN thread serves $\sim$5\,MOPS on the slower FDR NIC. The fact that the throughput gap is far smaller than the NIC bandwidth gap confirms that, in the same-rack topology, the system is \textbf{MN-CPU-bound}, not NIC-bound. (This conclusion holds for our 3-node same-rack setup; the 9-node multi-rack topology exposes a different regime where the MN is never the bottleneck --- see \S\ref{sec:repro-9node}.)

\subsubsection{Comparison to Paper Figure~10 (CX-3 cluster)}

The paper's Figure~10 uses r320 nodes with MX354A FDR (56\,Gbps), 4 MN threads, up to 64 CN threads. Our reproduction uses the \emph{same} hardware but with 1 MN thread and 2 CN nodes (32T max); the per-workload comparison is in Table~\ref{tab:paper-fig10} (Appendix~\ref{app:tables}).

Our single-MN-thread throughput \textbf{exceeds} the paper's Fig.~10 per-MN-thread rate by 5--19\% across all workloads, despite running only 2\,CN (32T) vs.~the paper's 8\,CN (64T). Since both use identical CX-3 56\,Gbps hardware, the NIC is not a factor. Two factors explain the per-thread advantage: (1)~we run a single dedicated MN thread without contention from other MN threads, whereas the paper's 4 MN threads share CPU cache and memory bus, reducing per-thread efficiency; and (2)~at one dedicated MN thread the workload is \emph{compute-bound at the MN} in the same-rack topology, so pure MN CPU capacity determines per-thread throughput. The paper reports that on CX-3, Outback outperforms RACE by 5.03$\times$ (aggregate); the dotted lines in Figure~\ref{fig:rdma-ycsb-all} make this gap visible, as RACE saturates at $\sim$3--4\,MOPS even with 64 CN threads.

\subsection{Coroutine Effects (Paper Figure~13)}\label{sec:repro-coro}

Raw coroutine measurements (1CN and 2CN configurations at C=1, 2, 3) are in Tables~\ref{tab:rdma-coro-1cn}--\ref{tab:rdma-coro-2cn} (Appendix~\ref{app:tables}). Figure~\ref{fig:rdma-coro} shows the latency--throughput frontier.

\begin{figure}[H]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=6cm,
    xlabel={Throughput (MOPS)},
    ylabel={Mean Latency ($\mu$s)},
    xmin=0, xmax=5.5,
    ymin=0, ymax=25,
    grid=major, grid style={gray!20},
    legend style={at={(0.02,0.98)},anchor=north west,font=\small,legend columns=2},
    every axis plot/.append style={mark size=2.5pt, thick},
    title={RDMA Coroutine Latency--Throughput (MT=1, YCSB-C)},
    legend style={at={(0.02,0.98)},anchor=north west,font=\scriptsize,legend columns=3}
]
% 3-node CX-3 (filled markers, 1MN+2CN, same-rack, tab:rdma-coro-2cn)
\addplot[color=rdmacolor!60,mark=triangle*,dashed]
  coordinates {(1.409,2.12)(2.808,2.09)(4.443,2.18)(4.870,6.01)};
\addplot[color=rdmacolor,mark=square*]
  coordinates {(2.802,2.18)(4.269,3.09)(4.833,6.75)(5.040,13.63)};
\addplot[color=rdmacolor!40!black,mark=diamond*,dashdotted]
  coordinates {(3.238,3.08)(4.196,5.10)(4.224,10.85)(4.414,21.18)};
% 9-node CX-3 (hollow dotted, 1MN+8CN, multi-rack, tab:9node-coro)
\addplot[color=rdmacolor!60,mark=triangle,dotted]
  coordinates {(2.261,3.0)(3.341,4.1)(4.246,7.2)(4.735,13.7)};
\addplot[color=rdmacolor,mark=square,dotted]
  coordinates {(2.427,6.1)(3.433,9.0)(4.254,15.2)};
\addplot[color=rdmacolor!40!black,mark=diamond,dotted]
  coordinates {(2.539,9.1)(3.630,13.1)(4.257,23.3)};
% Paper Fig.~13a (CX-6, MT=1, digitized) -- thin green overlay
\addplot[color=papercolor!70,mark=none,thin]
  coordinates {(0.5,1.0)(2.5,1.0)(4.0,1.5)(4.5,2.5)(5.0,10)(5.1,24)};
\addplot[color=papercolor,mark=none,thin,dashed]
  coordinates {(0.5,1.0)(3.0,1.0)(4.5,1.5)(5.0,2.5)(5.3,10)(5.5,24)};
\addplot[color=papercolor!30!black,mark=none,thin,dashdotted]
  coordinates {(0.5,1.0)(3.0,1.0)(4.5,2.0)(4.8,5.0)(5.0,24)};
\legend{3n\,C=1, 3n\,C=2, 3n\,C=3, 9n\,C=1, 9n\,C=2, 9n\,C=3, P\,C=1, P\,C=2, P\,C=3}
% Thread-count labels on 3-node C=2 curve
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:2.802,2.18) {4T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:4.269,3.09) {8T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:4.833,6.75) {16T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:5.040,13.63) {32T};
\end{axis}
\end{tikzpicture}}
\caption{RDMA coroutine latency--throughput (MT=1, YCSB-C). Filled markers = 3-node (1MN+2CN, same-rack $\sim$2\,$\mu$s RTT, 4--32T); hollow dotted = 9-node (1MN+8CN, multi-rack $\sim$29\,$\mu$s RTT, 8--64T); thin green = paper Fig.~13a digitized (CX-6, r650). The 9-node curves start at elevated latency ($\sim$3--9\,$\mu$s baseline vs.\ $\sim$2\,$\mu$s for 3-node) and plateau below 4.8\,MOPS despite $2\times$ more CN threads --- the multi-rack RTT caps throughput regardless of MN CPU state. Thread counts labeled on 3-node C=2 curve.}
\label{fig:rdma-coro}
\end{figure}

\begin{figure*}[t]
\centering
\begin{tikzpicture}
\begin{groupplot}[
    group style={group size=2 by 1, horizontal sep=1.5cm},
    width=0.45\textwidth,
    height=6cm,
    xlabel={Throughput (MOPS)},
    ylabel={Mean Latency ($\mu$s)},
    ymin=0,
    grid=major, grid style={gray!20},
    legend style={at={(0.02,0.98)},anchor=north west,font=\scriptsize,legend columns=3},
    every axis plot/.append style={mark size=2.5pt, thick}
]
% MT=1, 3-node 2CN + 9-node 8CN (tab:rdma-coro-2cn, tab:9node-coro)
\nextgroupplot[title={MT=1: 3-node (2CN) vs.\ 9-node (8CN)},xmin=0,xmax=5.5,ymax=25]
\addplot[color=rdmacolor!50,mark=triangle*,dashed]
  coordinates {(1.409,2.12)(2.808,2.09)(4.443,2.18)(4.870,6.01)};
\addplot[color=rdmacolor,mark=square*]
  coordinates {(2.802,2.18)(4.269,3.09)(4.833,6.75)(5.040,13.63)};
\addplot[color=rdmacolor!30!black,mark=diamond*,dashdotted]
  coordinates {(3.238,3.08)(4.196,5.10)(4.224,10.85)(4.414,21.18)};
% 9-node MT=1 (hollow dotted, 1MN+8CN, tab:9node-coro)
\addplot[color=rdmacolor!50,mark=triangle,dotted]
  coordinates {(2.261,3.0)(3.341,4.1)(4.246,7.2)(4.735,13.7)};
\addplot[color=rdmacolor,mark=square,dotted]
  coordinates {(2.427,6.1)(3.433,9.0)(4.254,15.2)};
\addplot[color=rdmacolor!30!black,mark=diamond,dotted]
  coordinates {(2.539,9.1)(3.630,13.1)(4.257,23.3)};
% Paper Fig.~13a: all 3 coroutine curves (CX-6, MT=1, digitized)
\addplot[color=papercolor!70,mark=none,thin]
  coordinates {(0.5,1.0)(2.5,1.0)(4.0,1.5)(4.5,2.5)(5.0,10)(5.1,24)};
\addplot[color=papercolor,mark=none,thin,dashed]
  coordinates {(0.5,1.0)(3.0,1.0)(4.5,1.5)(5.0,2.5)(5.3,10)(5.5,24)};
\addplot[color=papercolor!30!black,mark=none,thin,dashdotted]
  coordinates {(0.5,1.0)(3.0,1.0)(4.5,2.0)(4.8,5.0)(5.0,24)};
\legend{3n\,C=1,3n\,C=2,3n\,C=3,9n\,C=1,9n\,C=2,9n\,C=3,P\,C=1,P\,C=2,P\,C=3}
% Thread-count labels on 3-node C=2 curve (MT=1)
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:2.802,2.18) {4T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:4.269,3.09) {8T};
\node[font=\tiny,anchor=west,rdmacolor]  at (axis cs:4.833,6.75) {16T};
\node[font=\tiny,anchor=west,rdmacolor]  at (axis cs:5.040,13.63) {32T};
% MT=2, 3-node 2CN + 9-node 8CN (tab:rdma-mt2-coro, tab:9node-coro)
\nextgroupplot[title={MT=2: 3-node (2CN) vs.\ 9-node (8CN)},xmin=0,xmax=10,ymax=25]
\addplot[color=rdmacolor!50,mark=triangle*,dashed]
  coordinates {(1.423,2.12)(2.791,2.17)(5.436,2.32)(7.772,3.95)};
\addplot[color=rdmacolor,mark=square*]
  coordinates {(2.823,2.14)(5.390,2.27)(8.333,3.15)(8.266,8.04)};
\addplot[color=rdmacolor!30!black,mark=diamond*,dashdotted]
  coordinates {(4.044,2.18)(6.802,3.07)(7.933,6.12)(8.449,12.26)};
% 9-node MT=2 (hollow dotted, 1MN+8CN, tab:9node-coro)
\addplot[color=rdmacolor!50,mark=triangle,dotted]
  coordinates {(2.453,2.9)(3.327,4.2)(4.029,7.5)(4.594,14.0)};
\addplot[color=rdmacolor,mark=square,dotted]
  coordinates {(2.504,5.9)(3.381,9.2)(4.103,15.8)};
\addplot[color=rdmacolor!30!black,mark=diamond,dotted]
  coordinates {(2.574,9.0)(3.597,13.5)(4.039,23.7)};
% Paper Fig.~13b: all 3 coroutine curves (CX-6, MT=2, digitized)
\addplot[color=papercolor!70,mark=none,thin]
  coordinates {(0.5,1.0)(4.0,1.0)(7.0,1.5)(8.0,3.0)(9.0,12)(9.2,24)};
\addplot[color=papercolor,mark=none,thin,dashed]
  coordinates {(0.5,1.0)(4.0,1.0)(7.5,1.5)(8.5,3.0)(9.3,12)(9.5,24)};
\addplot[color=papercolor!30!black,mark=none,thin,dashdotted]
  coordinates {(0.5,1.0)(4.0,1.0)(7.5,2.0)(8.5,5.0)(8.8,12)(9.0,24)};
\legend{3n\,C=1,3n\,C=2,3n\,C=3,9n\,C=1,9n\,C=2,9n\,C=3,P\,C=1,P\,C=2,P\,C=3}
% Thread-count labels on 3-node C=2 curve (MT=2)
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:2.823,2.14) {4T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:5.390,2.27) {8T};
\node[font=\tiny,anchor=south,rdmacolor] at (axis cs:8.333,3.15) {16T};
\node[font=\tiny,anchor=west,rdmacolor]  at (axis cs:8.266,8.04) {32T};
\end{groupplot}
\end{tikzpicture}
\caption{RDMA latency--throughput (YCSB-C, MT=1 left, MT=2 right). Filled markers = 3-node (1MN+2CN, same-rack $\sim$2\,$\mu$s RTT); hollow dotted = 9-node (1MN+8CN, multi-rack $\sim$29\,$\mu$s RTT); thin green = paper Fig.~13 digitized (CX-6, r650). \textbf{Left (MT=1):} 3-node C=2 peaks at 5.04\,MOPS; 9-node C=2 plateaus at 4.54--4.65\,MOPS at elevated baseline latency --- RTT-limited, not MN-CPU-limited. \textbf{Right (MT=2):} 3-node scales to 8.3--8.4\,MOPS (1.64$\times$ over MT=1), confirming MN CPU is the bottleneck; 9-node MT=2 curves overlap almost exactly with MT=1 ($\leq$4.6\,MOPS), proving the MN CPU is idle in the multi-rack case. Hollow dotted curves span up to 64T (8--64T); filled markers span 4--32T.}
\label{fig:rdma-coro-latency}
\end{figure*}

\subsection{Memory Node Thread Scaling (Paper Figure~12)}\label{sec:repro-mt}

Thread-level measurements at MT=1 and MT=2 are in Tables~\ref{tab:rdma-memthreads}--\ref{tab:rdma-mt2-coro} (Appendix~\ref{app:tables}). With 2 MN threads, the system scales to $\sim$8.4\,MOPS at 32 threads (1.64$\times$ over 1 MN thread). This confirms that, in the same-rack 3-node topology, the MN CPU thread is the primary bottleneck, not the NIC. This MN-thread scaling disappears completely in the 9-node multi-rack topology (\S\ref{sec:repro-9node}), where RTT inflation makes the client the binding constraint. Figure~\ref{fig:rdma-coro-latency} (right panel) illustrates this MT=2 scaling pattern.

\subsection{Real-World Datasets (Paper Figure~11)}\label{sec:repro-datasets}

Facebook (FB) and OpenStreetMap (OSM) datasets were tested under 50\,M keys with uniform distribution. Zipfian workload was found \textbf{non-functional} for these datasets (code only activates zipfian parameters for YCSB workloads). Full per-thread and sensitivity measurements are in Tables~\ref{tab:rdma-fb}--\ref{tab:rdma-dataset-extra} (Appendix~\ref{app:tables}).

Dataset results (3-node same-rack) closely match YCSB-C, confirming throughput is MN-CPU-bound in the same-rack topology and independent of data distribution. Notably, \textbf{KV=80M causes an OOM crash} on the Memory Node's (MN) 16\,GB DRAM. (It is important to note that while the CN process consumes only $\sim$900\,MB, the physical memory boundary is hit strictly on the MN side.) The paper tests 80M on r650 with 256\,GB, a fact not disclosed. At 60M keys with LF=0.80, a severe slowdown occurred (throughput dropping to $\sim$2,945\,ops/s with $\sim$9.8\,ms latency), consistent with the working set spilling out of physical memory.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=6cm,
    ylabel={Throughput (MOPS)},
    xlabel={Number of CN Threads},
    xmode=log, log basis x=2,
    xtick={1,2,4,8,16,32,72,144},
    xticklabels={1,2,4,8,16,32,72,144},
    x tick label style={rotate=30,anchor=east,font=\tiny},
    xmin=1, xmax=200,
    ymin=0, ymax=7,
    legend style={at={(0.98,0.02)},anchor=south east,font=\tiny},
    every axis plot/.append style={mark size=2.5pt, thick},
    grid=major, grid style={gray!20},
    title={RDMA Dataset Scaling vs.\ Paper Fig.~11 (uniform)}
]
% RDMA reproduction (solid = 1CN, dashed = 2CN)
\addplot[color=rdmacolor,mark=square*]
  coordinates {(1,0.731)(2,1.418)(4,2.773)(8,4.541)(16,4.679)};
\addplot[color=rdmacolor,mark=square,dashed]
  coordinates {(4,2.737)(8,4.085)(16,4.620)(32,4.821)};
\addplot[color=rdmacolor!50!black,mark=triangle*]
  coordinates {(1,0.730)(2,1.405)(4,2.803)(8,4.514)(16,4.436)};
\addplot[color=rdmacolor!50!black,mark=triangle,dashed]
  coordinates {(4,2.745)(8,4.104)(16,4.741)(32,4.807)};
% Paper Fig.~11 Outback curves (CX-6, 1MT, uniform, digitized)
\addplot[color=papercolor,mark=none,very thick,densely dashed]
  coordinates {(8,5.0)(12,5.3)(20,5.6)(72,5.9)(108,6.0)(144,6.0)};
\addplot[color=papercolor!60!black,mark=none,very thick,densely dotted]
  coordinates {(8,5.0)(12,5.3)(20,5.6)(72,5.8)(108,6.0)(144,6.0)};
\legend{FB 1CN, FB 2CN, OSM 1CN, OSM 2CN, Paper FB (Outback), Paper OSM (Outback)}
\end{axis}
\end{tikzpicture}
\caption{RDMA dataset scaling vs.\ paper Fig.~11 (uniform). Solid/hollow markers = our r320 reproduction (1CN and 2CN). Thick dashed/dotted green lines = paper Outback on FB (dashed) and OSM (dotted) at up to 144T. Our r320 saturates at $\sim$4.8\,MOPS (32T, 2CN) vs.\ paper's CX-6 peak of $\sim$6.0\,MOPS (144T). FB and OSM are near-identical in both platforms, confirming that throughput is MN-CPU-bound and dataset-independent.}
\label{fig:rdma-dataset-scaling}
\end{figure}

\subsection{DMPH Memory Usage (Paper Figure~16)}\label{sec:repro-memory}

A custom DMPH index monitor was developed since the original source code lacked one. Measured DMPH index sizes and client process RSS are in Tables~\ref{tab:rdma-dmph}--\ref{tab:rdma-rss} (Appendix~\ref{app:tables}).

The DMPH index itself is small (e.g., 15.95\,MB for 20M keys at LF=0.85), but the actual client process consumes \textbf{915.8\,MB} for 60M keys --- over \textbf{14$\times$} the DMPH index size. Step-wise index size jumps (e.g., 60M and 80M keys giving the same index size) are caused by power-of-two bucket expansion.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=5.5cm,
    ylabel={DMPH Index Size (MB)},
    xlabel={Number of KV Pairs (Millions)},
    xtick={20,40,60,80,100},
    ymin=0, ymax=80,
    legend style={at={(0.98,0.02)},anchor=south east,font=\small},
    every axis plot/.append style={mark size=2.5pt, thick},
    grid=major, grid style={gray!20},
    title={DMPH Index Size Scaling}
]
\addplot[color=numacolor!60,mark=triangle*]
  coordinates {(20,15.48)(40,30.95)(60,61.88)(80,61.88)(100,61.88)};
\addplot[color=numacolor,mark=square*]
  coordinates {(20,15.95)(40,31.88)(60,63.75)(80,63.75)(100,63.75)};
\addplot[color=rdmacolor!60,mark=diamond*]
  coordinates {(20,16.42)(40,32.82)(60,32.82)(80,65.62)(100,65.62)};
\addplot[color=rdmacolor,mark=*]
  coordinates {(20,16.42)(40,32.82)(60,32.82)(80,65.62)(100,65.62)};
% Paper Fig 16 (estimated from figure)
\addplot[papercolor,densely dashed,thick,mark=star]
  coordinates {(20,12.5)(40,25)(60,37)(80,50)(100,58)};
\legend{LF=0.80,LF=0.85,LF=0.90,LF=0.95,Paper Fig~16}
\end{axis}
\end{tikzpicture}
\caption{DMPH index size: our measurements vs.\ paper's Fig~16 (green dashed). The paper shows smooth near-linear growth ($\sim$12.5\,MB at 20M, $<$60\,MB at 100M), while our measurements show step-wise jumps from power-of-two bucket expansion. Our values are $\sim$24--72\% higher than the paper's, suggesting additional overhead from the extendible hashing implementation.}
\label{fig:rdma-memory}
\end{figure}

\subsection{Resizing During Operation (Paper Figure~17)}\label{sec:repro-resize}

Resizing was tested with YCSB-D (5\% Insert) using 20M keys (as in the paper). The resize code exists only on a \textbf{separate branch} of the repository, not the main artifact branch; it is hard-coded to 30-second benchmarks, is incomplete, and is not representative of the paper's reported behavior. The standard main-branch experiments run \emph{without} resizing enabled. These RDMA resize results should therefore be treated as \textbf{partial reproduction evidence} from an experimental branch, not a full reproduction of Figure~17. For comparison, the CXL/NUMA resize is our own functional state-machine prototype (\S\ref{sec:resize-sm}).

\begin{table}[H]
\centering
\caption{RDMA resize: throughput disruption pattern (20M keys, 1MN 1CN, coro=2)}
\label{tab:rdma-resize}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}rrrrrr@{}}
\toprule
\textbf{Threads} & \textbf{Pre-Resize} & \textbf{During Resize} & \textbf{Post-Resize} & \textbf{Drop} & \textbf{Cycle} \\
 & \textbf{(MOPS)} & \textbf{(MOPS)} & \textbf{(MOPS)} & & \\
\midrule
4  & 1.39 & 0.75 & 1.54 & 46\% & $\sim$13\,s \\
8  & 2.37 & 1.45 & 2.95 & 39\% & $\sim$10\,s \\
12 & 2.89 & 1.80 & 3.71 & 38\% & $\sim$10\,s \\
16 & 3.04 & 2.00 & 4.19 & 34\% & $\sim$10\,s \\
\bottomrule
\end{tabular}}
\end{table}

Key observations:
\begin{itemize}[nosep]
  \item Post-resize throughput \emph{exceeds} pre-resize throughput (e.g., 2.95 vs.\ 2.37\,MOPS at 8T), followed by gradual decay as the table fills again.
  \item Resize frequency converges to $\sim$10\,s cycles for 8--16 threads; 4 threads show $\sim$13\,s cycles due to slower insert rate.
  \item The paper's Figure~17 shows a relatively smooth $\sim$52\% drop lasting $\sim$3\,s; our 4-thread results show a similar $\sim$46\% drop, but higher thread counts recover with large post-resize spikes that \emph{overshoot} pre-resize throughput by up to 38\% (e.g., 16T: 4.20\,MOPS post vs.\ 3.04\,MOPS pre). The paper shows no such overshoot, suggesting the branch used for our reproduction differs from the version tested in the paper.
\end{itemize}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=7cm,
    ylabel={Throughput (MOPS)},
    xlabel={Time (seconds)},
    ymin=0, ymax=4.8,
    xmin=0, xmax=47,
    grid=major, grid style={gray!20},
    title={RDMA Resize Time Series (20M keys)},
    legend style={at={(0.98,0.98)},anchor=north east,font=\scriptsize},
    clip=false
]
% Thread 4
\addplot[color=rdmacolor!50,mark=none,thick,dashed] coordinates {
  (0,1.394)(1,1.396)(2,1.389)(3,1.384)(4,1.386)(5,1.377)
  (6,1.378)(7,1.371)(8,1.372)(9,1.367)(10,0.990)(11,0.752)
  (12,0.761)(13,1.480)(14,1.537)(15,1.540)(16,1.381)(17,1.364)
  (18,1.358)(19,1.353)(20,1.350)(21,1.351)(22,1.349)(23,1.336)
  (24,1.131)(25,0.753)(26,0.749)(27,1.316)(28,1.545)(29,1.541)
  (30,1.412)(31,1.338)(32,1.334)(33,1.331)(34,1.330)(35,1.328)
  (36,1.324)(37,1.222)(38,0.744)(39,0.755)(40,1.167)(41,1.542)
  (42,1.545)(43,1.453)(44,1.316)(45,1.321)(46,1.320)(47,1.321)
};
\addlegendentry{4T}
% Thread 8
\addplot[color=rdmacolor,mark=none,thick] coordinates {
  (0,2.352)(1,2.400)(2,2.366)(3,2.367)(4,2.337)(5,2.333)
  (6,1.551)(7,1.449)(8,1.767)(9,2.957)(10,2.953)(11,2.952)
  (12,2.348)(13,2.303)(14,2.300)(15,2.282)(16,2.268)
  (17,1.499)(18,1.454)(19,1.877)(20,2.955)(21,2.959)(22,2.954)
  (23,2.272)(24,2.254)(25,2.248)(26,2.224)
  (27,1.773)(28,1.428)(29,1.471)(30,2.848)(31,2.948)(32,2.953)
  (33,2.447)(34,2.209)(35,2.200)
};
\addlegendentry{8T}
% Thread 12
\addplot[color=rdmacolor!60!black,mark=none,thick,dashdotted] coordinates {
  (0,2.892)(1,2.817)(2,2.773)(3,2.745)(4,2.732)
  (5,1.911)(6,1.796)(7,2.129)(8,3.702)(9,3.687)(10,3.710)
  (11,2.778)(12,2.649)(13,2.624)(14,2.622)
  (15,2.149)(16,1.751)(17,1.738)(18,3.456)(19,3.700)(20,3.723)
  (21,3.082)(22,2.601)(23,2.576)(24,2.539)
  (25,1.974)(26,1.730)(27,1.852)(28,3.694)(29,3.699)(30,3.703)
  (31,2.836)(32,2.503)
};
\addlegendentry{12T}
% Thread 16
\addplot[color=rdmacolor!30!black,mark=none,thick,dotted] coordinates {
  (0,3.041)(1,3.037)(2,3.034)(3,2.980)
  (4,2.776)(5,2.025)(6,2.016)(7,3.249)(8,4.193)(9,4.202)
  (10,3.850)(11,2.895)(12,2.860)(13,2.818)
  (14,2.632)(15,2.001)(16,1.990)(17,3.263)(18,4.130)(19,4.175)
  (20,3.783)(21,2.780)(22,2.742)(23,2.727)
  (24,2.247)(25,1.987)(26,1.994)(27,4.068)(28,4.151)(29,4.194)
  (30,3.176)(31,2.658)
};
\addlegendentry{16T}
% Paper Fig.~17 curves (CX-6, r650, digitized -- cover 0-24s)
\addplot[color=papercolor!60,mark=none,thin]
  coordinates {
  (0,2.2)(3,2.2)(5.5,1.5)(6,1.5)(7,1.8)(8,2.1)(10,2.2)
  (12,2.0)(12.5,1.5)(13.5,1.8)(15,2.1)(17,2.2)
  (18,1.5)(18.5,1.5)(19.5,1.8)(21,2.2)(24,2.2)};
\addlegendentry{Paper 8T (CX-6)}
\addplot[color=papercolor,mark=none,thin,dashed]
  coordinates {
  (0,2.8)(3,2.7)(5,2.3)(6,1.8)(7,2.0)(8,2.7)(10,2.5)
  (12,2.0)(13,2.2)(14.5,2.5)(17,2.5)
  (18,2.0)(19,2.2)(21,2.5)(24,2.8)};
\addlegendentry{Paper 12T (CX-6)}
\addplot[color=papercolor!40!black,mark=none,thin,dashdotted]
  coordinates {
  (0,4.0)(3,4.0)(4.5,3.5)(5.5,2.0)(6,1.8)(7,2.5)(8,4.2)(12,4.2)
  (12.5,2.5)(13,2.2)(14,3.5)(15,4.2)(17,4.2)
  (18,3.5)(18.5,2.0)(19,2.0)(20.5,3.8)(21,4.2)(24,4.2)};
\addlegendentry{Paper 16T (CX-6)}
\end{axis}
\end{tikzpicture}
\caption{RDMA resize time series vs.\ paper Fig.~17. \textbf{Bold colored lines} = our CX-3 reproduction (4T/8T/12T/16T). \textbf{Thin green lines} = paper Fig.~17 digitized (CX-6, 8:1/12:1/16:1 CN:MN, first 24\,s shown). Paper curves are remarkably smooth at 2--4\,MOPS with $\sim$1.5\,s resize dips ($\sim$32--52\% drop). Our reproduction shows erratic recovery spikes overshooting pre-resize throughput by up to 38\% (e.g., 16T peaks at 4.20\,MOPS post-resize vs.\ 3.04\,MOPS pre-resize), likely from the resizing code being on a separate branch. Thread count ordering is consistent: more threads $\to$ higher steady-state, more frequent resizes, and larger post-resize spikes.}
\label{fig:rdma-resize-ts}
\end{figure}

\subsection{Reproduction Summary}

Table~\ref{tab:repro-summary} summarizes the key discrepancies between the paper's claims and our RDMA reproduction.

\begin{table}[H]
\centering
\caption{Reproduction findings: paper claims vs.\ our RDMA measurements}
\label{tab:repro-summary}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}p{2.0cm}p{2.0cm}p{4.5cm}@{}}
\toprule
\textbf{Paper Claim} & \textbf{Published Value} & \textbf{Our RDMA Finding} \\
\midrule
5.03$\times$ over RACE & YCSB-C, CX-3 & Consistent per-MN-thread rate; ratio untested (baselines not reproduced) \\
6.01\,MOPS peak & Fig.~9c, CX-6 & 5.04\,MOPS on CX-3 at 32T (0.84$\times$); gap from $\sim$2$\times$ NIC (CX-3 56\,Gbps FDR vs.~CX-6 100\,Gbps) \\
Linear scaling & To 144 CN threads & Saturates at $\sim$5\,MOPS (32T) due to MN CPU; confirmed MN-bound \\
MN thread scaling & Fig.~12 (CX-6 r650); Fig.~10 (CX-3 r320) & Confirmed with same-rack topology (3-node: 1.64$\times$ at MT=2); \emph{absent} in multi-rack 9-node ($\sim$29\,$\mu$s RTT, flat at 4.5--4.8\,MOPS for MT=1--4; coroutine sweep C=1--3 shows no improvement; gap vs.\ paper's Fig.~10 \emph{plausibly} from cross-rack CloudLab placement --- same-rack allocation would likely reduce RTT toward the $\sim$2\,$\mu$s regime and may close much of the gap) \\
Smooth resize ($\sim$52\%) & Figure~17 & $\sim$45\% drop with erratic recovery; code on separate branch \\
12.5\,MB memory/20M & Figure~16 & DMPH index $=$ 15.95--16.42\,MB at 20M (RDMA, LF=0.85--0.95); process RSS reaches 915.8\,MB at 60M \\
Coroutines essential & Figure~13 & 3-node (same-rack): coro=1$\to$2 substantially improves throughput in the unsaturated region by hiding RDMA RTT; near MN-thread saturation, additional coroutines increase latency without improving peak throughput. 9-node (multi-rack): C=1/2/3 all plateau at 4.4--4.8\,MOPS; coroutines do not help when RTT is the ceiling \\
Write performance & YCSB-A, F & YCSB-F degrades at 32T (below 16T 2CN peak) \\
Code completeness & Implied & Resize on separate branch; broken zipfian; no YCSB-E \\
\bottomrule
\end{tabular}}
\end{table}

\textbf{Key takeaways:} Our RDMA reproduction \emph{confirms} the paper's core architectural insight (DMPH enables single-RTT reads that scale with MN threads) but reveals undisclosed limitations in memory overhead, write workload degradation, codebase completeness, and hardware requirements.

\subsection{9-Node Full-Scale Experiments (Paper Fig.~10 Topology)}\label{sec:repro-9node}

To directly match the paper's Fig.~10 topology (1\,MN + 8\,CN r320 nodes, CX-3 56\,Gbps FDR, 8\,T/CN = 64 total CN threads), we ran YCSB, MN-thread scaling, and coroutine experiments on the full 9-node CloudLab cluster. Dataset experiments (FB/OSM) failed due to dataset unavailability on the cluster and are excluded. The 9-node results reveal an important bottleneck absent in the same-rack 3-node setup: multi-rack RTT inflation.

\subsubsection{YCSB Peak Throughput (64 Total CN Threads)}

Peak aggregate throughput across all 5 YCSB workloads at 64 total CN threads (8\,CN $\times$ 8\,T/CN, coro=2) is in Table~\ref{tab:9node-ycsb-peak} (Appendix~\ref{app:tables}). YCSB-C peaks at 4.752\,MOPS (MT=2) --- slightly below our 3-node result of 5.04\,MOPS at 32T despite $2\times$ the CN threads. The throughput dropped because the multi-rack RTT ($\sim$29\,$\mu$s vs.\ $\sim$2\,$\mu$s) imposed a client-side ceiling that additional CN threads cannot overcome.

\subsubsection{MN Thread Scaling is Absent at 29\,$\mu$s RTT}

Table~\ref{tab:9node-mt-scaling} (Appendix~\ref{app:tables}) shows YCSB-C MN-thread scaling with 64 CN threads (coro=2). Throughput is essentially flat across MT=1--4: the dedicated MN-thread sweep (Table~\ref{tab:9node-mt-scaling}) measures 4.537--4.681\,MOPS, and the per-workload peak sweep (Table~\ref{tab:9node-ycsb-peak}) measures 4.571--4.752\,MOPS. The $\sim$5\% spread between the two runs reflects run-to-run variance at the multi-rack RTT-bound plateau, not MN-thread scaling. This contrasts sharply with the same-rack 3-node result (MT=1: 5.04\,MOPS $\to$ MT=2: 8.27\,MOPS, 1.64$\times$ scaling).

The root cause is \textbf{multi-rack RTT}: the 9-node cluster spans multiple APT racks, yielding $\sim$29\,$\mu$s application-level RTT vs.\ $\sim$2\,$\mu$s for the same-rack 3-node topology. With coro=2 and 29\,$\mu$s RTT, the theoretical per-thread throughput ceiling is:
\[
  \frac{\text{coros}}{\text{RTT}} = \frac{2}{29\,\mu\text{s}} \approx 68{,}966\ \text{ops/s/thread}
\]
Across 64 CN threads: $64 \times 68{,}966 \approx 4.41$\,MOPS. Our measured plateau of 4.54--4.75\,MOPS slightly exceeds this estimate, which is consistent with the 29\,$\mu$s figure being a \emph{mean} application-level RTT observed under load rather than the minimum hardware RTT; when queues are not fully saturated, the effective RTT is slightly lower, allowing marginally higher throughput. The small discrepancy is therefore not a violation of the bound --- it illustrates that the 29\,$\mu$s average is a slightly conservative proxy, and the system is nonetheless firmly in the network-bound regime. In this multi-rack topology, the MN never becomes the bottleneck; the RTT-imposed client ceiling is reached long before MN CPU is saturated, so adding MN threads has no effect. This is the opposite of the same-rack 3-node case (\S\ref{sec:repro-mt}), where adding a second MN thread yields a 1.64$\times$ throughput gain.

\subsubsection{Coroutine Sweep Confirms Client Saturation}

Table~\ref{tab:9node-coro} (Appendix~\ref{app:tables}) shows the Fig.~13 coroutine sweep on 8 CNs (64 max total threads). All three coroutine counts (C=1/2/3) plateau at 4.4--4.7\,MOPS at 64\,T. The hockey-stick latency shape is preserved (e.g.\ MT=1 C=2: 6.1\,$\mu$s at 8T $\to$ 29.1\,$\mu$s at 64T), but unlike the 3-node case where C=1$\to$2 substantially improves throughput in the unsaturated region (with diminishing returns near MN-thread saturation), here all coroutine counts converge to the same ceiling. This indicates the bottleneck in the 9-node setup is not a straightforward client-side ceiling that more coroutines can alleviate: adding coroutines increases queuing latency proportionally, leaving throughput unchanged. The gap between our measured aggregate plateau of $\sim$4.6\,MOPS and the paper's Fig.~10 result on identical r320 CX-3 9-node hardware ($\sim$17\,MOPS aggregate at 4 MN threads, 64 CN threads) has a \textbf{probable physical explanation}: CloudLab's default node scheduler allocates resources based on real-time cluster availability, dispersing nodes across different physical racks and spine switches. This is consistent with our measured $\sim$29\,$\mu$s RTT. The original authors may have secured a same-rack allocation, preserving the $\sim$2\,$\mu$s intra-rack RTT seen in our 3-node setup. At 2\,$\mu$s RTT with coro=2, the per-thread ceiling rises to $2/2\,\mu\text{s}=1\,\text{MOPS/thread}$, yielding $\sim$64\,MOPS aggregate, which --- with 4 MN threads removing the MN CPU bottleneck --- is fully consistent with the paper's 17\,MOPS figure. To reproduce this result, a same-rack placement constraint (e.g., a \texttt{same-switch} or \texttt{same-rack} colocation hint in the CloudLab NS RSpec) would be required when requesting 9+ nodes.

% ══════════════════════════════════════════════════════════════════════════════
\section{Stress Tests and Breaking Points}\label{sec:stress}
% ══════════════════════════════════════════════════════════════════════════════

Beyond the paper's designed operating envelope, two critical memory limits were identified. (1)~\textbf{OOM at 80M keys (RDMA):} The r320 Memory Node's (MN) 16\,GB DRAM is insufficient for 80M KV pairs once the raw KV array, DMPH index, and pre-registered RDMA hugepage MR are all resident simultaneously on the server --- the paper tests 80M only on r650 (256\,GB) without disclosing this constraint. (2)~\textbf{Swap thrashing at 60M keys:} At 60M keys with LF=0.80, throughput collapsed from $\sim$4.5\,MOPS to $\sim$2,945\,ops/s ($\sim$9.8\,ms latency) --- a \textbf{1,500$\times$} slowdown from memory swapping. Additional fragility points (write degradation at scale, coroutine overload, CXL resize stalls, range queries) are detailed in Sections~\ref{sec:codebase-issues}, \ref{sec:repro-coro}, \ref{sec:repro-mt}, and the multi-platform comparative analysis (Section~\ref{sec:multi-platform}).

% ══════════════════════════════════════════════════════════════════════════════
\section{CXL/NUMA Extension Results}\label{sec:cxl-results}
% ══════════════════════════════════════════════════════════════════════════════

This section presents the CXL/NUMA extension results, which go beyond reproducing the paper's RDMA experiments. By eliminating the network stack, we test whether the DMPH index architecture can scale to much higher throughput when the RDMA bottleneck is removed.

\subsection{YCSB Throughput}

\subsubsection{YCSB-C (100\% Read)}

Full per-thread measurements (Tput, Mean/P99/P999 latency) are in Table~\ref{tab:numa-ycsbc} (Appendix~\ref{app:tables}).
\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6cm,
    ylabel={Throughput (MOPS)},
    xlabel={Number of Threads},
    symbolic x coords={1,2,4,8,16,32},
    xtick=data,
    ymin=0, ymax=140,
    bar width=10pt,
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=45,anchor=south west},
    title={CXL/NUMA YCSB-C Scaling}
]
\addplot[fill=numacolor!80] coordinates {
  (1,4.794) (2,9.056) (4,17.833) (8,35.737) (16,70.091) (32,118.270)
};
\end{axis}
\end{tikzpicture}
\caption{CXL/NUMA YCSB-C throughput exhibits near-perfect linear scaling up to 32 threads (118\,MOPS), with no NIC bottleneck. For comparison, the paper's Outback peaks at 6.01\,MOPS with 144 threads on CX-6 (Fig.~9c); our 32-thread CXL/NUMA result is \textbf{19.7$\times$} higher with fewer than one-quarter the thread count. This should be interpreted as an optimistic upper-bound architectural comparison rather than a hardware-normalized CXL-vs-RDMA result: the NUMA proxy eliminates PCIe/CXL controller overhead and uses local DDR4 bandwidth.}
\label{fig:numa-ycsbc-bar}
\end{figure}

\subsection{Loop Batch Size Effect (CXL Port --- Formerly Coro)}

Raw C=1/2/3 measurements are in Table~\ref{tab:numa-coro} (Appendix~\ref{app:tables}).

The batching loop is a vestigial artifact of the coroutine-to-synchronous conversion: rather than removing the outer \texttt{coro} loop entirely when porting from RDMA to CXL/NUMA, we converted it to a synchronous \texttt{for}-loop with a configurable batch count (\texttt{Batch=1/2/3}). The results below confirm it can be stripped out entirely without any performance penalty; the code simplification is left as future work.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=6cm,
    ylabel={Throughput (MOPS)},
    xlabel={Number of Threads},
    xmode=log, log basis x=2,
    xtick={1,2,4,8,16,32},
    xticklabels={1,2,4,8,16,32},
    ymin=0, ymax=140,
    legend style={at={(0.02,0.98)},anchor=north west,font=\small},
    every axis plot/.append style={mark size=2.5pt, thick},
    title={CXL/NUMA: Loop Batch Size Effect --- Negligible}
]
\addplot[color=numacolor!60,mark=triangle*,dashed]
  coordinates {(1,4.776)(4,17.734)(8,35.827)(16,70.214)(32,116.106)};
\addplot[color=numacolor,mark=square*]
  coordinates {(1,4.794)(4,17.833)(8,35.737)(16,70.091)(32,118.270)};
\addplot[color=numacolor!40!black,mark=diamond*,dashdotted]
  coordinates {(1,4.743)(4,17.675)(8,35.399)(16,69.548)(32,121.286)};
\legend{Batch=1, Batch=2, Batch=3}
\end{axis}
\end{tikzpicture}
\caption{The batch-size parameter (Batch=1/2/3, replacing the RDMA \texttt{coro} count) has virtually no effect on CXL/NUMA throughput --- all three curves overlap. Direct load/store access over NUMA is fast enough ($\sim$0.13\,$\mu$s) that no latency-hiding is needed, confirming the batching loop is a purely vestigial structure with no performance role. By contrast, in the RDMA port, increasing coro=1$\to$2 substantially improves throughput by hiding $\sim$2--5\,$\mu$s network round-trips; this optimization is architecturally irrelevant when the transport is sub-microsecond load/store.}
\label{fig:numa-coro}
\end{figure}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=6cm,
    xlabel={Throughput (MOPS)},
    ylabel={Mean Latency ($\mu$s)},
    xmin=0, xmax=130,
    ymin=0.10, ymax=0.20,
    grid=major, grid style={gray!20},
    legend style={at={(0.02,0.98)},anchor=north west,font=\small},
    every axis plot/.append style={mark size=2.5pt, thick},
    title={CXL/NUMA: Latency vs.\ Throughput}
]
\addplot[color=numacolor!60,mark=triangle*,dashed]
  coordinates {(4.776,0.126)(9.198,0.131)(17.734,0.138)(35.827,0.138)(70.214,0.140)(116.106,0.155)};
\addplot[color=numacolor,mark=square*]
  coordinates {(4.794,0.126)(9.056,0.135)(17.833,0.137)(35.737,0.139)(70.091,0.141)(118.270,0.153)};
\addplot[color=numacolor!40!black,mark=diamond*,dashdotted]
  coordinates {(4.743,0.126)(9.223,0.130)(17.675,0.137)(35.399,0.138)(69.548,0.140)(121.286,0.152)};
\legend{Batch=1, Batch=2, Batch=3}
\end{axis}
\end{tikzpicture}
\caption{CXL/NUMA latency--throughput (cf.\ Paper Fig.~13 style). All three batch-size curves (Batch=1/2/3) overlap almost perfectly: latency remains at 0.13--0.15\,$\mu$s regardless of batch size, even as throughput scales from 5 to 121\,MOPS. The slight uptick at 32 threads ($\sim$0.15\,$\mu$s) is caused by memory bus contention, not batching overhead. Compare with the RDMA plot (Figure~\ref{fig:rdma-coro-latency}) where latency explodes to 21\,$\mu$s at the same throughput ceiling.}
\label{fig:numa-coro-latency}
\end{figure}

\subsection{All YCSB Workloads}

Per-workload measurements (B, A, D, F at 4--32 threads) are in Table~\ref{tab:numa-ycsb-all} (Appendix~\ref{app:tables}).

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=7cm,
    ylabel={Throughput (MOPS)},
    xlabel={Number of Threads},
    xmode=log, log basis x=2,
    xtick={1,2,4,8,16,32},
    xticklabels={1,2,4,8,16,32},
    ymin=0, ymax=150,
    legend style={at={(0.02,0.98)},anchor=north west,font=\small},
    every axis plot/.append style={mark size=2.5pt, thick},
    grid=major,
    grid style={gray!30},
    title={CXL/NUMA: Throughput Across YCSB Workloads}
]
\addplot[color=numacolor,mark=square*]
  coordinates {(1,4.794)(2,9.056)(4,17.833)(8,35.737)(16,70.091)(32,118.270)};
\addplot[color=papercolor,mark=triangle*]
  coordinates {(4,17.775)(8,35.772)(16,69.087)(32,122.821)};
\addplot[color=orange,mark=diamond*]
  coordinates {(1,2.470)(2,5.269)(4,10.422)(8,21.909)(16,44.183)(32,85.514)};
\addplot[color=purple!80,mark=pentagon*]
  coordinates {(1,4.764)(2,9.628)(4,19.691)(8,40.854)(16,82.002)(32,129.707)};
\addplot[color=rdmacolor,mark=star]
  coordinates {(1,1.970)(2,4.051)(4,8.460)(8,18.189)(16,31.935)(32,46.775)};
\legend{YCSB-C, YCSB-B, YCSB-A, YCSB-D, YCSB-F}
\end{axis}
\end{tikzpicture}
\caption{CXL/NUMA workload comparison. Read-dominated workloads (C, B, D) scale near-linearly past 100\,MOPS. The write-heavy YCSB-F plateaus around 47\,MOPS due to locking overhead. YCSB-A (50\% writes) sits in between at 85\,MOPS. Compared to the paper's Outback peaks on CX-6 (YCSB-C: 6.01, YCSB-B: 5.82, YCSB-A: 5.50, YCSB-D: $\sim$5.9, YCSB-F: 3.62\,MOPS at 144\,T), CXL/NUMA achieves \textbf{13--22$\times$} higher throughput on every workload with only 32 threads (optimistic upper bound; hardware, topology, and CXL controller overhead differ).}
\label{fig:numa-ycsb-all}
\end{figure}

\subsection{Dataset Sensitivity}

Full sensitivity measurements (KV count, load factor, real datasets) are in Table~\ref{tab:numa-datasets} (Appendix~\ref{app:tables}).

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6cm,
    ylabel={Throughput (MOPS)},
    symbolic x coords={KV=20M,KV=50M,KV=80M,LF=0.75,LF=0.85,LF=0.95},
    xtick=data,
    x tick label style={rotate=30, anchor=east, font=\small},
    ymin=0, ymax=170,
    bar width=11pt,
    legend style={at={(0.5,-0.22)},anchor=north,font=\small,legend columns=2},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=45,anchor=south west},
    title={CXL/NUMA: Dataset Sensitivity (32 threads)}
]
\addplot[fill=numacolor!70] coordinates {
  (KV=20M,149.266)(KV=50M,118.108)(KV=80M,100.621)
  (LF=0.75,124.817)(LF=0.85,121.532)(LF=0.95,118.108)
};
\addplot[fill=papercolor!70] coordinates {
  (KV=20M,150.242)(KV=50M,118.017)(KV=80M,101.690)
  (LF=0.75,124.982)(LF=0.85,121.216)(LF=0.95,118.017)
};
\legend{Facebook, OSM}
\end{axis}
\end{tikzpicture}
\caption{Throughput is sensitive to working-set size (20M$\to$80M shows $\sim$33\% drop due to L3 cache pressure) but insensitive to load factor and real-vs-synthetic distribution. The paper's Fig.~11 reports $\sim$6.0\,MOPS for uniform FB/OSM throughput at 144 threads on CX-6; our 32-thread CXL/NUMA result at 50M keys ($\sim$118\,MOPS) is $\sim$\textbf{20$\times$} higher. Even at 80M keys (100.6\,MOPS), CXL/NUMA is \textbf{16.8$\times$} the paper's peak.}
\label{fig:numa-datasets}
\end{figure}

\subsection{Resize Behavior}

\begin{table}[H]
\centering
\caption{CXL/NUMA resize experiments (20M keys, s\_slow=58\%, s\_stop=65\%). Trigger = seconds into 120s run when first resize was triggered. Cumul.\ Stall Time = total seconds at zero throughput across all resize events in the 120s run; individual stall durations are 2--12\,s per event (see Figure~\ref{fig:numa-resize-ts}). \textbf{Mean (MOPS) is averaged over active-service windows only} (zero-throughput stall intervals are excluded from the average); for reference, the time-weighted mean over the full 120\,s window would be $\sim$40--58\% lower (e.g., 16T: $24.957\times(120{-}74)/120\approx9.6$\,MOPS).}
\label{tab:numa-resize}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}rrrrr@{}}
\toprule
\textbf{T} & \textbf{Mean (MOPS)} & \textbf{Max (MOPS)} & \textbf{Trigger (s)} & \textbf{Cumul. Stall Time (s)} \\
\midrule
8  & 13.127 & 20.387 & 16 & 67 \\
12 & 17.628 & 30.250 & 14 & 66 \\
16 & 24.957 & 39.838 & 14 & 74 \\
\bottomrule
\end{tabular}}
\end{table}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=7cm,
    ylabel={Throughput (MOPS)},
    xlabel={Time (seconds)},
    ymin=0, ymax=44,
    xmin=0, xmax=119,
    grid=major, grid style={gray!20},
    title={CXL Resize Time Series (20M keys)},
    legend style={at={(0.98,0.98)},anchor=north east,font=\scriptsize},
]
% 8 threads
\addplot[color=numacolor,mark=none,thick,dashed] coordinates {
  (0,20.35)(1,20.39)(2,20.27)(3,20.19)(4,13.02)(5,16.74)
  (6,18.54)(7,18.42)(8,18.35)(9,18.28)(10,17.55)(11,17.36)
  (12,4.92)(13,10.99)(14,18.21)(15,18.09)(16,18.03)(17,17.97)
  (18,17.93)(19,17.88)(20,17.84)(21,17.51)(22,17.02)(23,17.01)
  (24,16.98)(25,14.31)(26,0)(27,0.28)(28,17.95)(29,17.78)
  (30,17.72)(31,17.68)(32,17.68)(33,17.62)(34,17.59)(35,17.35)
  (36,16.86)(37,16.85)(38,16.84)(39,16.82)(40,16.81)(41,16.80)
  (42,16.81)(43,16.11)(44,2.38)(45,0)(46,0)(47,0)
  (48,14.03)(49,17.43)(50,16.90)(51,16.88)(52,16.86)(53,16.84)
  (54,16.83)(55,16.81)(56,16.83)(57,16.81)(58,16.82)(59,16.83)
  (60,16.79)(61,16.80)(62,16.79)(63,16.77)(64,16.66)(65,15.98)
  (66,10.66)(67,0)(68,0)(69,0)(70,0)(71,0)
  (72,0)(73,0)(74,2.46)(75,17.01)(76,16.89)(77,16.87)
  (78,16.83)(79,16.81)(80,16.82)(81,16.79)(82,16.79)(83,16.78)
  (84,16.79)(85,16.79)(86,16.76)(87,16.79)(88,16.78)(89,16.77)
  (90,16.79)(91,16.77)(92,16.78)(93,16.77)(94,16.78)(95,16.79)
  (96,16.79)(97,16.81)(98,16.79)(99,16.78)(100,16.79)(101,16.78)
  (102,16.78)(103,16.47)(104,15.96)(105,15.99)(106,15.62)(107,5.89)
};
\addlegendentry{8T}
% 12 threads
\addplot[color=numacolor!70!black,mark=none,thick] coordinates {
  (0,30.23)(1,30.25)(2,30.04)(3,13.08)(4,26.31)(5,26.07)
  (6,25.92)(7,25.00)(8,24.79)(9,7.10)(10,9.18)(11,25.71)
  (12,25.53)(13,25.38)(14,25.33)(15,25.25)(16,25.15)(17,25.10)
  (18,24.74)(19,24.20)(20,24.16)(21,24.12)(22,22.09)(23,0)
  (24,0)(25,13.14)(26,24.95)(27,24.94)(28,24.91)(29,24.86)
  (30,24.86)(31,24.82)(32,24.62)(33,24.20)(34,24.17)(35,24.19)
  (36,24.15)(37,24.18)(38,24.18)(39,24.14)(40,23.59)(41,8.49)
  (42,0)(43,0)(44,0)(45,0)(46,19.01)(47,24.08)
  (48,24.02)(49,23.97)(50,23.98)(51,23.95)(52,23.94)(53,23.95)
  (54,23.94)(55,23.92)(56,23.93)(57,23.92)(58,23.91)(59,23.90)
  (60,23.90)(61,23.92)(62,23.18)(63,22.75)(64,4.41)(65,0)
  (66,0)(67,0)(68,0)(69,0)(70,0)(71,0)
  (72,0)(73,0.33)(74,24.23)(75,24.05)(76,24.02)(77,24.00)
  (78,23.98)(79,23.96)(80,23.94)(81,23.97)(82,23.95)(83,23.97)
  (84,23.98)(85,23.95)(86,23.96)(87,23.96)(88,23.95)(89,23.96)
  (90,23.94)(91,23.97)(92,23.97)(93,23.97)(94,23.99)(95,23.98)
  (96,23.96)(97,23.97)(98,23.97)(99,23.95)(100,23.95)(101,23.78)
  (102,22.90)(103,22.88)(104,22.74)(105,13.57)
};
\addlegendentry{12T}
% 16 threads
\addplot[color=numacolor!40!black,mark=none,thick,dashdotted] coordinates {
  (0,39.84)(1,39.79)(2,18.07)(3,31.38)(4,33.28)(5,32.92)
  (6,31.61)(7,31.47)(8,16.58)(9,0)(10,26.47)(11,32.50)
  (12,32.38)(13,32.29)(14,32.17)(15,32.14)(16,32.07)(17,31.79)
  (18,30.82)(19,30.79)(20,30.73)(21,30.70)(22,30.03)(23,0.42)
  (24,0)(25,0)(26,27.82)(27,31.77)(28,31.70)(29,31.70)
  (30,31.67)(31,31.64)(32,31.49)(33,30.86)(34,30.51)(35,30.47)
  (36,30.44)(37,30.47)(38,30.43)(39,30.47)(40,30.48)(41,30.43)
  (42,30.09)(43,20.64)(44,0)(45,0)(46,0)(47,0)
  (48,0)(49,6.82)(50,30.46)(51,30.36)(52,30.34)(53,30.34)
  (54,30.34)(55,30.45)(56,30.44)(57,30.43)(58,30.41)(59,30.42)
  (60,30.42)(61,30.42)(62,30.41)(63,30.39)(64,30.42)(65,30.40)
  (66,30.42)(67,30.44)(68,29.69)(69,29.15)(70,11.15)(71,0)
  (72,0)(73,0)(74,0)(75,0)(76,0)(77,0)
  (78,0)(79,0)(80,0)(81,0)(82,25.24)(83,29.40)
  (84,30.42)(85,30.40)(86,30.43)(87,30.42)(88,30.41)(89,30.42)
  (90,30.41)(91,30.38)(92,30.39)(93,30.43)(94,30.47)(95,30.45)
  (96,30.46)(97,30.55)(98,30.49)(99,30.52)(100,30.52)(101,30.49)
  (102,30.50)(103,30.50)(104,30.49)(105,30.49)(106,30.48)(107,30.48)
  (108,30.48)(109,30.51)(110,30.50)(111,30.48)(112,30.56)(113,30.61)
  (114,30.57)(115,30.65)(116,29.89)(117,29.31)(118,29.35)(119,28.92)
};
\addlegendentry{16T}
\end{axis}
\end{tikzpicture}
\caption{CXL/NUMA resize time series for 8, 12, and 16 threads. Resize events cause throughput to drop to near zero (a near-complete stall). Early resize events recover in 2--4\,s; later resizes take progressively longer as the table grows and more data must be copied --- 4--8\,s by the third resize and up to $\sim$12\,s for the 16-thread R4 stall (sec 71--82). Higher thread counts reach higher steady-state throughput but trigger resizes more frequently. In contrast, the paper's RDMA resize (Fig.~17) shows a $\sim$52\% \emph{partial} throughput drop lasting $\sim$3\,s with service maintained; CXL/NUMA stalls fully but recovers atomically once the remap completes.}
\label{fig:numa-resize-ts}
\end{figure}


% ══════════════════════════════════════════════════════════════════════════════
\section{Multi-Platform Comparative Analysis}\label{sec:multi-platform}
% ══════════════════════════════════════════════════════════════════════════════

This section compares five hardware configurations grouped into four platform categories --- paper-reported results (r650 and r320 clusters), our 3-node RDMA reproduction, our 9-node RDMA full-scale experiments, and our CXL/NUMA extension --- for direct side-by-side comparison. Where the RDMA reproduction (Section~\ref{sec:repro-ycsb}) and the 9-node topology experiments (\S\ref{sec:repro-9node}) focused on validating the paper's claims, this section adds the CXL/NUMA dimension and draws the combined architectural implications.

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Peak YCSB Throughput: All Platforms}
% ──────────────────────────────────────────────────────────────────────────────

Table~\ref{tab:three-way-peaks} consolidates the paper's reported peaks, the paper's baselines, and all three of our experiment platforms for all five YCSB workloads. A key result is that the 9-node RDMA peak falls \emph{below} the 3-node result despite $2\times$ more CN threads: multi-rack RTT ($\sim$29\,$\mu$s) with coro=2 makes the client the binding bottleneck, capping aggregate throughput at $\sim$4.6\,MOPS regardless of MN-thread count (\S\ref{sec:repro-9node}).

\begin{table}[H]
\centering
\caption{Peak throughput across all platforms (MOPS per shard)}
\label{tab:three-way-peaks}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrrrr@{}}
\toprule
\textbf{Workload} & \textbf{Paper Outback} & \textbf{Paper Cluster} & \textbf{RDMA 3-node} & \textbf{RDMA 9-node} & \textbf{CXL/NUMA} & \textbf{CXL vs Paper} \\
 & \textbf{(CX-6, 144T)} & \textbf{(CX-6, 144T)} & \textbf{(r320, 32T)} & \textbf{(r320, 64T)} & \textbf{(32T)} & \\
\midrule
YCSB-A & 5.50 & 5.14 & 4.049 & 3.783 & 85.514 & \textbf{15.5$\times$} \\
YCSB-B & 5.82 & 5.49 & 4.439 & 4.181 & 122.821 & \textbf{21.1$\times$} \\
YCSB-C & 6.01 & 5.41 & 5.040 & 4.752 & 118.270 & \textbf{19.7$\times$} \\
YCSB-D & $\sim$5.9 & $\sim$5.40 & 4.281 & 4.073 & 129.707 & \textbf{$\sim$22$\times$} \\
YCSB-F & 3.62 & 3.64 & 2.354 & 2.530 & 46.775 & \textbf{12.9$\times$} \\
\bottomrule
\end{tabular}}
\end{table}

\begin{figure}[H]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=7cm,
    ylabel={Throughput (MOPS)},
    symbolic x coords={YCSB-A,YCSB-B,YCSB-C,YCSB-D,YCSB-F},
    xtick=data,
    ymin=0, ymax=140,
    bar width=5pt,
    legend style={at={(0.5,-0.22)},anchor=north,font=\scriptsize,legend columns=2},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=60,anchor=south west},
    title={Peak: Paper vs.\ RDMA (3-node/9-node) vs.\ CXL}
]
% Paper Outback
\addplot[fill=papercolor!80] coordinates {
  (YCSB-A,5.50)(YCSB-B,5.82)(YCSB-C,6.01)(YCSB-D,5.90)(YCSB-F,3.62)
};
% Paper Cluster
\addplot[fill=papercolor!50,postaction={pattern=dots}] coordinates {
  (YCSB-A,5.14)(YCSB-B,5.49)(YCSB-C,5.41)(YCSB-D,5.40)(YCSB-F,3.64)
};
% RDMA 3-node (32T, same-rack, ~2us RTT)
\addplot[fill=rdmacolor!80] coordinates {
  (YCSB-A,4.05)(YCSB-B,4.44)(YCSB-C,5.04)(YCSB-D,4.28)(YCSB-F,2.35)
};
% RDMA 9-node (64T, multi-rack, ~29us RTT) -- peaks lower despite 2x threads
\addplot[fill=orange!70] coordinates {
  (YCSB-A,3.783)(YCSB-B,4.181)(YCSB-C,4.752)(YCSB-D,4.073)(YCSB-F,2.530)
};
% CXL/NUMA (hatched = emulated NUMA proxy; full-scale values)
\addplot[fill=numacolor!25,postaction={pattern=north east lines,pattern color=numacolor!80}] coordinates {
  (YCSB-A,85.5)(YCSB-B,123)(YCSB-C,118)(YCSB-D,130)(YCSB-F,46.8)
};
\legend{Paper Outback (CX-6), Paper Cluster (CX-6), RDMA 3-node (r320{,}32T), RDMA 9-node (r320{,}64T), CXL/NUMA proxy (c6420{,} \emph{upper bound})}
\end{axis}
\end{tikzpicture}}%
\caption{Direct comparison to Paper Figure~9 across all platforms. Paper's Outback peaks at $\sim$6\,MOPS with 144 threads on CX-6. Our 3-node RDMA (32T, same-rack) reaches 2.35--5.04\,MOPS. Our 9-node RDMA (64T, multi-rack, \textbf{orange}) peaks \emph{lower} than 3-node on most workloads despite $2\times$ more CN threads --- a consequence of $\sim$29\,$\mu$s multi-rack RTT saturating the client at coro=2 before the MN is reached. CXL/NUMA (32T) reaches 118--130\,MOPS in the NUMA proxy, corresponding to 15--22$\times$ the paper's reported Outback throughput; this is an upper-bound architectural result, not a direct hardware comparison. \textbf{Hatched bars} indicate emulated CXL/NUMA proxy results (not real CXL hardware).}
\label{fig:paper-fig9-cmp}
\end{figure}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{YCSB-C Baselines Context}
% ──────────────────────────────────────────────────────────────────────────────

The paper's YCSB-C results (Figure~9c) are the most detailed, reporting baselines at 72 CN threads. We compare our results against these paper-reported baseline values; we did not directly reproduce RACE, MICA, or Cluster due to build-breaking issues (\S\ref{sec:codebase-issues}), so the speedup ratios over baselines are not independently verified.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6.5cm,
    ylabel={Throughput (MOPS)},
    symbolic x coords={MICA,RACE,Cluster,Outback,{RDMA Repro},{CXL 1T},{CXL 4T},{CXL 8T},{CXL 32T}},
    xtick=data,
    x tick label style={rotate=45,anchor=east,font=\scriptsize},
    ymin=0, ymax=130,
    bar width=8pt,
    legend style={at={(0.5,-0.22)},anchor=north,font=\tiny,legend columns=3},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=45,anchor=south west,inner sep=1pt},
    title={YCSB-C Baselines vs.\ Our Platforms}
]
\addplot[fill=papercolor!30] coordinates {
  (MICA,2.47)(RACE,4.59)(Cluster,5.41)(Outback,6.01)
};
\addplot[fill=rdmacolor!70] coordinates {
  ({RDMA Repro},5.04)
};
\addplot[fill=numacolor!25,postaction={pattern=north east lines,pattern color=numacolor!80}] coordinates {
  ({CXL 1T},4.79)({CXL 4T},17.83)({CXL 8T},35.74)({CXL 32T},118.27)
};
\legend{Paper (CX-6{,} 72T), RDMA Repro (r320{,} 32T), CXL/NUMA (c6420)}
\end{axis}
\end{tikzpicture}
\caption{Positioning our results among the paper's baselines. \textbf{Note: RACE, MICA, and Cluster values are digitized directly from the original paper (CX-6 100\,Gbps hardware, 72 CN threads) as their source code could not be compiled in our environment; CXL/NUMA values are our measured NUMA-proxy results (c6420, local DDR4).} Our RDMA reproduction (5.04\,MOPS) falls between the paper's RACE (4.59) and Cluster (5.41) baselines. CXL/NUMA with just \textbf{1 thread} (4.79\,MOPS) already surpasses both the paper's RACE and MICA baselines outright, and matches the paper's Outback result at approximately 50 threads (interpolated from Fig.~9c). At 32 threads, CXL/NUMA is 19.7$\times$ the paper's Outback peak. These speedup ratios are not independently verified against the baselines. \textbf{Hatched bars} indicate emulated CXL/NUMA proxy results (not real CXL hardware).}
\label{fig:baselines-detail}
\end{figure}

% ──────────────────────────────────────────────────────────────────────────────
% Moved CX-3 comparison into Section 4 (reproduction)
% ──────────────────────────────────────────────────────────────────────────────
\subsection{Throughput Scaling: All Platforms}
% ──────────────────────────────────────────────────────────────────────────────

Detailed YCSB-C measurements across all platforms are in Table~\ref{tab:three-way} (Appendix~\ref{app:tables}).

\begin{figure}[H]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=7.5cm,
    ylabel={Throughput (MOPS)},
    xlabel={Total Client Threads},
    xmode=log, log basis x=2,
    xtick={1,2,4,8,16,32,64,128},
    xticklabels={1,2,4,8,16,32,64,144},
    ymin=0, ymax=155,
    legend style={at={(0.5,-0.22)},anchor=north,legend columns=2,font=\scriptsize},
    every axis plot/.append style={mark size=3pt, thick},
    grid=major,
    grid style={gray!25},
    title={Multi-Platform YCSB-C Scaling: Two RDMA Regimes vs.\ CXL}
]
% Paper CX-6 Outback (estimated from Fig 9c)
\addplot[color=papercolor,mark=triangle*,line width=1.5pt]
  coordinates {(8,1.2)(12,1.8)(20,2.8)(64,5.8)(128,6.01)};
% Paper CX-6 RACE baseline
\addplot[color=papercolor!50,mark=triangle,dashed,thin]
  coordinates {(8,0.9)(12,1.3)(20,2.0)(64,4.5)(128,4.59)};
% Paper CX-6 Cluster baseline
\addplot[color=papercolor!70,mark=x,dashdotted,thin]
  coordinates {(8,1.1)(12,1.6)(20,2.5)(64,5.3)(128,5.41)};
% RDMA 3-node reproduction (same-rack, ~2us RTT)
\addplot[color=rdmacolor,mark=square*,line width=1.5pt]
  coordinates {(1,0.724)(2,1.411)(4,2.770)(8,4.503)(16,4.325)(32,5.040)};
% RDMA 9-node (multi-rack, ~29us RTT, MT=1 coro=2): 8-64T
\addplot[color=orange,mark=x,mark options={scale=1.4,line width=0.9pt},dashed,line width=1.2pt]
  coordinates {(8,2.447)(16,3.397)(32,4.361)(64,4.655)};
% CXL/NUMA
\addplot[color=numacolor,mark=*,line width=1.5pt]
  coordinates {(1,4.794)(2,9.056)(4,17.833)(8,35.737)(16,70.091)(32,118.270)};
% Ideal linear from NUMA 1-thread
\addplot[color=gray!50,dashed,no marks,thin]
  coordinates {(1,4.794)(32,153.408)};
\legend{Paper Outback (CX-6), Paper RACE (CX-6), Paper Cluster (CX-6), RDMA 3-node (r320), RDMA 9-node (r320), CXL/NUMA (c6420), Ideal linear}
\end{axis}
\end{tikzpicture}}%
\caption{YCSB-C throughput scaling across all platforms. The paper's curves (green) plateau near 4.5--6\,MOPS, limited by the single MN thread's CPU. Our 3-node RDMA (solid red) reaches 5.04\,MOPS at 32T. Our 9-node RDMA (dashed orange, \S\ref{sec:repro-9node}) plateaus at 4.65\,MOPS at 64T despite $2\times$ more CN threads: the multi-rack RTT ($\sim$29\,$\mu$s, coro=2) saturates the client before the MN is reached. CXL/NUMA (blue) scales nearly linearly because it eliminates both the MN CPU bottleneck and the network RTT ceiling.}
\label{fig:three-way}
\end{figure}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Dataset Comparison}
% ──────────────────────────────────────────────────────────────────────────────

The paper's Figure~11 evaluates Get throughput on Facebook (FB) and OpenStreetMap (OSM) datasets (uniform and zipfian-0.99). Detailed platform-by-platform numbers are in Table~\ref{tab:paper-fig11} (Appendix~\ref{app:tables}).

Our RDMA reproduction shows 4.82\,MOPS (FB) and 4.81\,MOPS (OSM) at 32 threads --- consistent with the paper's per-MN-thread throughput. With 3 MN threads, RDMA reaches 10.84\,MOPS (FB) and 10.59\,MOPS (OSM). Our CXL/NUMA results at 32 threads (\textbf{118\,MOPS}) are \textbf{$\sim$20$\times$} the paper's peak. Notably, zipfian distribution for real datasets was found \textbf{non-functional} in the source code despite the paper reporting such results. The 9-node full-scale experiments could not evaluate FB/OSM datasets due to missing files on the CloudLab cluster; those 9-node results are excluded from this section.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6.5cm,
    ylabel={Throughput (MOPS)},
    symbolic x coords={FB uniform,OSM uniform,FB MT=2,OSM MT=2,FB MT=3,OSM MT=3},
    xtick=data,
    x tick label style={rotate=35, anchor=east, font=\scriptsize},
    ymin=0, ymax=140,
    bar width=6pt,
    legend style={at={(0.02,0.57)},anchor=north west,font=\scriptsize},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=40,anchor=south west,inner sep=1pt},
    title={Dataset Comparison (uniform)}
]
% Paper (CX-6, 144T, 2 shards): ~6 MOPS per shard
\addplot[fill=papercolor!70] coordinates {
  ({FB uniform},6.0)({OSM uniform},6.0)
  ({FB MT=2},9.89)({OSM MT=2},9.89)
  ({FB MT=3},14.0)({OSM MT=3},14.0)
};
% RDMA reproduction (r320, 32T, 1MN 2CN)
\addplot[fill=rdmacolor!70] coordinates {
  ({FB uniform},4.821)({OSM uniform},4.807)
  ({FB MT=2},7.918)({OSM MT=2},8.117)
  ({FB MT=3},10.844)({OSM MT=3},10.588)
};
% CXL/NUMA (c6420, 32T)
\addplot[fill=numacolor!70] coordinates {
  ({FB uniform},118.11)({OSM uniform},118.02)
  ({FB MT=2},119.45)({OSM MT=2},120.60)
  ({FB MT=3},118.38)({OSM MT=3},118.39)
};
\legend{Paper (CX-6{,} 144T), RDMA (r320{,} 32T), CXL/NUMA (c6420{,} 32T)}
\end{axis}
\end{tikzpicture}
\caption{Three-way comparison on real-world datasets (uniform distribution). CXL/NUMA achieves $\sim$118\,MOPS regardless of MN threads ($\sim$20$\times$ the paper's peak). The paper and our same-rack 3-node RDMA both scale linearly with MN threads, confirming MN CPU is the bottleneck in the same-rack RDMA regime. This scaling is absent in the 9-node multi-rack topology (\S\ref{sec:repro-9node}), where RTT inflation is the binding constraint. CXL/NUMA eliminates both the MN CPU bottleneck and the network RTT ceiling entirely.}
\label{fig:dataset-3way-cmp}
\end{figure}

Both the paper and our same-rack 3-node RDMA scale near-linearly with MN threads (MN CPU is the bottleneck in this regime), while CXL/NUMA shows $<$2\% variation. Note that our 9-node multi-rack RDMA does not scale with MN threads at all (\S\ref{sec:repro-9node}). Dataset identity (FB vs.\ OSM) has no measurable effect, confirming DMPH lookup cost is data-distribution-invariant under uniform access.

% ──────────────────────────────────────────────────────────────────────────────
\subsection{MN Thread Scalability: Topology Dependence}
% ──────────────────────────────────────────────────────────────────────────────

The paper's Figure~12 varies MN threads 1--3 (4$\times$ r650 with CX-6, 288 CN threads): Outback is 1.10--1.21$\times$ Cluster and $\sim$3$\times$ MICA, with throughput growing 6.01\,MOPS (MT=1) $\to$ 9.89\,MOPS (MT=2) $\to$ 14.0\,MOPS (MT=3) (peak at 3 MN threads). Note this is on different hardware (CX-6 r650) than our 9-node experiment (CX-3 r320, paper Fig.~10).

Our CXL/NUMA results show \textbf{no measurable impact} from mem\_threads ($<$2\% variance). In the CXL/NUMA port, \texttt{mem\_threads} no longer represents memory-node CPU threads; it is repurposed as \textbf{allocation-lane sharding} to reduce CAS contention on the insert counter. This has no effect on the read path and only limited effect on write-heavy workloads because the current implementation still has cache-line contention beyond the allocation counter --- the lane mechanism only partially addresses write contention. Our 3-node RDMA (same-rack, $\sim$2\,$\mu$s RTT) confirms the paper's trend: 1T: 4.82, 2T: 7.92, 3T: 10.84\,MOPS (near-linear, MN-CPU-bound). However, our 9-node RDMA experiment (\S\ref{sec:repro-9node}) reveals a critical topology dependence: with multi-rack RTT ($\sim$29\,$\mu$s) and coro=2, MN-thread scaling disappears completely --- 4.54--4.75\,MOPS for MT=1--4 across both 9-node runs (Tables~\ref{tab:9node-ycsb-peak},~\ref{tab:9node-mt-scaling}; intra-MT spread is $\sim$5\% and reflects run variance, not scaling). Furthermore, our coroutine sweep (C=1/2/3 at 64\,T) shows that increasing coroutine count in the 9-node topology does not recover throughput: all three counts converge at 4.4--4.7\,MOPS, with latency scaling proportionally. The paper's Fig.~10 linear MN-thread scaling on the same 9-node r320 CX-3 hardware (reaching $\sim$17\,MOPS at 4 MN threads) is therefore not explained by our experiments; the paper's benchmark configuration was not fully disclosed, and the gap remains an open discrepancy. Note that the Fig.~12 MN-thread comparison is \emph{not} hardware-matched: the paper's Fig.~12 uses r650/CX-6 (288 CN threads), whereas our 9-node experiment uses r320/CX-3 (64 CN threads); any numerical discrepancy relative to Fig.~12 should not be interpreted as a failure to reproduce Fig.~12. Without RPC dispatch, CXL/NUMA has no MN CPU bottleneck at all.

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    width=\columnwidth,
    height=6.5cm,
    ylabel={Throughput (MOPS)},
    symbolic x coords={{1 MN},{2 MN},{3 MN}},
    xtick=data,
    ymin=0, ymax=140,
    bar width=8pt,
    legend style={at={(0.98,0.75)},anchor=north east,font=\scriptsize},
    nodes near coords,
    nodes near coords style={font=\tiny,rotate=45,anchor=south west,inner sep=1pt},
    title={MN Thread Scalability}
]
% Paper Outback (est. from text: 1T~6 Mops, 2T~9.89, 3T~14)
\addplot[fill=papercolor!70] coordinates {
  ({1 MN},6.01)({2 MN},9.89)({3 MN},14.0)
};
% RDMA reproduction (FB dataset, 1MN 2CN 32T)
\addplot[fill=rdmacolor!70] coordinates {
  ({1 MN},4.82)({2 MN},7.92)({3 MN},10.84)
};
% CXL/NUMA (from Table 6, FB dataset, 32T)
\addplot[fill=numacolor!70] coordinates {
  ({1 MN},118.11)({2 MN},119.45)({3 MN},118.38)
};
\legend{Paper (CX-6), RDMA (r320), CXL/NUMA (c6420)}
\end{axis}
\end{tikzpicture}
\caption{Comparison to Paper Figure~12. Both the paper (288 CN threads) and our same-rack 3-node RDMA (32T) scale $\sim$linearly with MN threads (MN CPU is the bottleneck in the same-rack regime). Our 9-node multi-rack RDMA breaks this pattern: throughput is flat at 4.5--4.8\,MOPS for MT=1--4 because the RTT-imposed client ceiling is hit before MN CPU is saturated (\S\ref{sec:repro-9node}). CXL/NUMA is flat for a different reason --- no MN CPU bottleneck at all. Our 3-node RDMA at 3 MN threads (10.84\,MOPS) is comparable to the paper's 2 MN threads (9.89\,MOPS).}
\label{fig:paper-fig12-cmp}
\end{figure}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Coroutine Effects (Three-Way)}
% ──────────────────────────────────────────────────────────────────────────────

The paper's Figure~13 shows YCSB-C latency--throughput curves for varying coroutine counts: more coroutines increase throughput when CN threads $<$ 72 (hiding RDMA RTT), with max $\sim$6\,MOPS regardless of coroutine count at 1 MN thread, and latency doubling/tripling when MN CPU becomes the bottleneck at 216 threads.

\begin{figure*}[t]
\centering
\begin{tikzpicture}
\begin{groupplot}[
    group style={group size=2 by 1, horizontal sep=1.5cm},
    width=0.45\textwidth,
    height=6.5cm,
    xlabel={Throughput (MOPS)},
    ylabel={Mean Latency ($\mu$s)},
    ymin=0,
    grid=major, grid style={gray!20},
    legend style={at={(0.02,0.98)},anchor=north west,font=\scriptsize},
    every axis plot/.append style={mark size=2.5pt, thick}
]
% RDMA latency-vs-throughput (MT=1, 2CN)
\nextgroupplot[title={RDMA (MT=1, 2CN)},xmin=0,xmax=6,ymax=25]
\addplot[color=rdmacolor!50,mark=triangle*,dashed]
  coordinates {(1.409,2.12)(2.808,2.09)(4.443,2.18)(4.870,6.01)};
\addplot[color=rdmacolor,mark=square*]
  coordinates {(2.802,2.18)(4.269,3.09)(4.833,6.75)(5.040,13.63)};
\addplot[color=rdmacolor!30!black,mark=diamond*,dashdotted]
  coordinates {(3.238,3.08)(4.196,5.10)(4.224,10.85)(4.414,21.18)};
\legend{C=1,C=2,C=3}
% CXL latency-vs-throughput
\nextgroupplot[title={CXL/NUMA},xmin=0,xmax=130,ymin=0.10,ymax=0.20]
\addplot[color=numacolor!50,mark=triangle*,dashed]
  coordinates {(4.776,0.126)(17.734,0.138)(35.827,0.138)(70.214,0.140)(116.106,0.155)};
\addplot[color=numacolor,mark=square*]
  coordinates {(4.794,0.126)(17.833,0.137)(35.737,0.139)(70.091,0.141)(118.270,0.153)};
\addplot[color=numacolor!30!black,mark=diamond*,dashdotted]
  coordinates {(4.743,0.126)(17.675,0.137)(35.399,0.138)(69.548,0.140)(121.286,0.152)};
\legend{Batch=1,Batch=2,Batch=3}
\end{groupplot}
\end{tikzpicture}
\caption{Comparison to Paper Figure~13 (latency--throughput style). \textbf{Left:} On RDMA, coroutines shift the throughput--latency frontier: C=1 achieves 4.9\,MOPS at 6\,$\mu$s; C=2 reaches 5.0\,MOPS but at 13.6\,$\mu$s; C=3 saturates at 4.4\,MOPS with 21\,$\mu$s --- the MN CPU is overloaded. Note the ``hockey stick'' shape: latency is flat until throughput saturates, then rises steeply. \textbf{Right:} On CXL/NUMA, latency is flat at 0.13--0.15\,$\mu$s across all inner-loop batch sizes (Batch=1/2/3) and all throughput levels up to 121\,MOPS. There is no throughput--latency trade-off because no MN CPU bottleneck exists. This is the fundamental architectural advantage of CXL over RDMA.}
\label{fig:coro-sidebyside}
\end{figure*}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Sensitivity Analysis (Paper Figures~14--15)}
% ──────────────────────────────────────────────────────────────────────────────

\textbf{Load factor (Fig.~14):} Both paper ($\sim$6\,MOPS) and our RDMA (4.50--4.82\,MOPS) confirm trivial impact ($<$7\%) from LF 0.75--0.95. CXL/NUMA shows 5.4\% decrease (124.8$\to$118.1\,MOPS).

\textbf{KV count (Fig.~15):} Paper reports 3.2\% decrease (6.02$\to$5.83\,MOPS, 20M$\to$80M). Our RDMA OOMs at 80M (r320 has only 16\,GB DRAM); at 60M the server swaps, collapsing to $\sim$2,945\,ops/s ($\sim$9.8\,ms). CXL/NUMA shows 32.6\% decrease (149.3$\to$100.6\,MOPS) from L3 cache misses.

\begin{table}[H]
\centering
\caption{Paper Figures~14--15 vs.\ RDMA reproduction vs.\ CXL/NUMA: sensitivity}
\label{tab:paper-fig14-15}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}llrrr@{}}
\toprule
\textbf{Param} & \textbf{Variation} & \textbf{Paper (CX-6)} & \textbf{RDMA (r320)} & \textbf{CXL/NUMA} \\
\midrule
Load Factor & 0.75 $\to$ 0.95 & trivial ($<$1\%) & 6.6\% increase & 5.4\% decrease \\
KV Pairs & 20M $\to$ 80M    & 3.2\% decrease & OOM at 80M & \textbf{32.6\%} decrease \\
\bottomrule
\end{tabular}}
\end{table}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Memory Usage (Three-Way, Paper Figure~16)}
% ──────────────────────────────────────────────────────────────────────────────

The paper's Figure~16 plots compute-node DMPH index memory for 20M--100M keys at LF 0.80--0.95, claiming ``around 12.5\,MB'' at 20M and ``below 60\,MB'' at 100M. A four-way comparison (paper formula, paper Fig.~16 estimates, RDMA, CXL) is in Table~\ref{tab:fig16-cmp} (Appendix~\ref{app:tables}).

\begin{figure*}[t]
\centering
\begin{tikzpicture}
\begin{groupplot}[
    group style={group size=2 by 1, horizontal sep=1.5cm},
    width=0.45\textwidth,
    height=5.5cm,
    xlabel={KV Pairs (Millions)},
    ylabel={DMPH Index Size (MB)},
    xtick={20,40,60,80,100},
    ymin=0, ymax=75,
    grid=major, grid style={gray!20},
    legend style={at={(0.98,0.02)},anchor=south east,font=\scriptsize},
    every axis plot/.append style={thick}
]
% LF=0.85
\nextgroupplot[title={Load Factor = 0.85}]
\addplot[color=papercolor,dashed,mark=o,mark size=2pt]
  coordinates {(20,11.17)(40,22.33)(60,33.50)(80,44.66)(100,55.83)};
\addlegendentry{Paper Formula}
\addplot[color=papercolor!50!black,densely dashed,mark=pentagon*,mark size=2pt]
  coordinates {(20,12.5)(40,25)(60,37)(80,50)(100,58)};
\addlegendentry{Paper Fig.~16 (est.)}
\addplot[color=rdmacolor,mark=square*,mark size=2.5pt]
  coordinates {(20,15.95)(40,31.88)(60,63.75)(80,63.75)(100,63.75)};
\addlegendentry{RDMA Measured}
\addplot[color=numacolor,mark=triangle*,mark size=2.5pt,densely dotted]
  coordinates {(20,15.93)(40,31.87)(60,63.73)(80,63.73)(100,63.73)};
\addlegendentry{CXL/NUMA Measured}
% LF=0.95
\nextgroupplot[title={Load Factor = 0.95}]
\addplot[color=papercolor,dashed,mark=o,mark size=2pt]
  coordinates {(20,10.57)(40,21.15)(60,31.72)(80,42.30)(100,52.87)};
\addlegendentry{Paper Formula}
\addplot[color=papercolor!50!black,densely dashed,mark=pentagon*,mark size=2pt]
  coordinates {(20,12.5)(40,25)(60,37)(80,50)(100,58)};
\addlegendentry{Paper Fig.~16 (est.)}
\addplot[color=rdmacolor,mark=square*,mark size=2.5pt]
  coordinates {(20,16.42)(40,32.82)(60,32.82)(80,65.62)(100,65.62)};
\addlegendentry{RDMA Measured}
\addplot[color=numacolor,mark=triangle*,mark size=2.5pt,densely dotted]
  coordinates {(20,16.87)(40,33.73)(60,33.73)(80,67.47)(100,67.47)};
\addlegendentry{CXL/NUMA Measured}
\end{groupplot}
\end{tikzpicture}
\caption{Comparison to Paper Figure~16: four-way memory comparison. The paper's theoretical formula (open circles) predicts smooth linear growth. The paper's own Figure~16 measured values (pentagons, estimated from stated anchors) are $\sim$10\% above the formula. Our RDMA and CXL/NUMA measurements (filled markers) show \textbf{step-wise jumps} caused by power-of-2 bucket allocation. \textbf{Left (LF=0.85):} At 60M keys the bucket count doubles ($2^{24} \to 2^{25}$), causing the index to jump from $\sim$32 to $\sim$64\,MB --- 72\% above the paper's measured value. \textbf{Right (LF=0.95):} The jump occurs between 40M and 80M. At 100M keys, both platforms exceed the paper's stated ``$<$60\,MB'' (65.6--67.5\,MB).}
\label{fig:paper-fig16-cmp}
\end{figure*}

Three key discrepancies between the paper's claims and our measurements: (1)~\textbf{Power-of-2 allocation} --- bucket counts double at crossing boundaries (e.g., 60M at LF=0.85 triggers $2^{24}\!\to\!2^{25}$ buckets), causing the index to jump from $\sim$32 to $\sim$64\,MB while the paper predicts smooth $\sim$50\% growth. (2)~\textbf{Overprovisioning} --- our measurements (15.5--16.9\,MB at 20M) are 24--35\% above the paper's Figure~16 values and 34--55\% above the formula, due to power-of-2 Othello hash array sizing and lock array overhead. (3)~\textbf{Plateau behavior} --- because bucket counts scale in powers of two, the index size remains identical across wide ranges of key counts before jumping at the next power-of-two boundary; this occurs at every load factor, not only LF$\leq$0.85. For example, at LF=0.80, the index is 61.88\,MB for 60M, 80M, and 100M keys alike; at LF=0.90, it is 32.82\,MB for both 40M and 60M keys. Millions of keys can therefore be added with zero additional memory cost --- a feature invisible in the paper's smoothed figure. RDMA and CXL/NUMA differ by at most $\sim$16\,KB, confirming the DMPH data structure is transport-agnostic.

In addition, the actual RDMA client \emph{process} RSS far exceeds the DMPH index: 364.6\,MB for 20M keys and 915.8\,MB for 60M keys (at LF=0.85), which is 23$\times$ and 14$\times$ the DMPH index, respectively. (Note that this $\sim$1\,GB footprint is strictly Compute Node overhead, completely independent of the server-side memory pressure that causes the 80M key MN crashes mentioned in Section~\ref{sec:stress}.) The CXL/NUMA client avoids this overhead entirely --- no RDMA buffer registration, no QP connection state, and no coroutine stacks are needed. The paper does not report process-level memory at all, presenting only the DMPH index as the compute-node memory cost.

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Resize Comparison (Paper Figure~17)}
% ──────────────────────────────────────────────────────────────────────────────

The paper's Figure~17 tests YCSB-D (5\% Insert) with 8, 12, and 16 CN threads. The paper states: ``it takes around 3 seconds to recalculate the bucket locator and the seed for each bucket'' and ``Outback still supports partial Get requests during resizing with a decreased throughput by approximately 52\%.'' However, the paper's Figure~17 visually shows a relatively smooth throughput dip.

\begin{table}[H]
\centering
\caption{Resizing disruption: Paper Figure~17 vs.\ our measurements}
\label{tab:resize-cmp}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}llll@{}}
\toprule
\textbf{Metric} & \textbf{Paper (Fig.~17)} & \textbf{RDMA (r320)} & \textbf{CXL/NUMA (c6420)} \\
\midrule
Tput drop & $\sim$52\% & $\sim$45\% & $\sim$95--100\% (full stall) \\
Duration & $\sim$3\,s & 2--3\,s & 2--12\,s (grows with table size) \\
Threads tested & 8, 12, 16 & 4, 8, 12, 16 & 8, 12, 16 \\
Recovery & Smooth return & Erratic spikes & Atomic resume after remap \\
Continuity & Partial Gets & Partial Gets & Full stall then instant \\
\bottomrule
\end{tabular}}
\end{table}

The detailed resize time series are shown in Figure~\ref{fig:rdma-resize-ts} (RDMA, 4/8/12/16 threads) and Figure~\ref{fig:numa-resize-ts} (CXL/NUMA, 8/12/16 threads). The key difference is clear: RDMA resize causes a $\sim$45\% throughput drop lasting 2--3\,s with partial Get service maintained during the transition, while CXL/NUMA shows a near-complete stall ($\sim$95--100\%) lasting 2--12\,s --- short for early resizes (2--4\,s) but growing as the table fills (up to $\sim$12\,s for the 16-thread fourth resize, see Fig.~\ref{fig:numa-resize-ts}) because the shared-memory remap blocks all clients atomically. Each individual stall is sharp but recovery is instantaneous once the remap completes.

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Latency Comparison}
% ──────────────────────────────────────────────────────────────────────────────

\begin{table}[H]
\centering
\caption{Latency comparison at 8 threads, YCSB-C}
\label{tab:latency-cmp}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrr@{}}
\toprule
\textbf{Metric} & \textbf{RDMA (r320)} & \textbf{CXL/NUMA (c6420)} & \textbf{Improvement} \\
\midrule
Mean Latency     & 3.04\,$\mu$s & 0.139\,$\mu$s & 21.9$\times$ \\
P99 Latency (est.)& $\sim$6\,$\mu$s & 0.50\,$\mu$s & $\sim$12$\times$ \\
\bottomrule
\end{tabular}}
\end{table}

\begin{figure}[H]
\centering
\begin{tikzpicture}
\begin{axis}[
    width=\columnwidth,
    height=6.5cm,
    xlabel={Throughput (MOPS)},
    ylabel={Mean Latency ($\mu$s)},
    xmin=0, xmax=130,
    ymin=0, ymax=55,
    grid=major, grid style={gray!20},
    title={Tput vs.\ Latency (Three-Way)},
    legend style={at={(0.98,0.98)},anchor=north east,font=\small},
    mark size=3pt,
]
% RDMA 1CN coro=2
\addplot[color=rdmacolor!60,mark=triangle*,thick,dashed] coordinates {
  (0.724,2.06)(1.411,2.11)(2.770,2.15)(4.503,3.04)(4.325,6.69)
};
\addlegendentry{RDMA 1CN}
% RDMA 2CN coro=2
\addplot[color=rdmacolor,mark=square*,thick] coordinates {
  (2.802,2.14)(4.269,3.19)(4.833,6.75)(5.040,13.63)
};
\addlegendentry{RDMA 2CN}
% CXL/NUMA coro=2
\addplot[color=numacolor,mark=*,thick] coordinates {
  (4.794,0.126)(9.056,0.135)(17.833,0.137)(35.737,0.139)(70.091,0.141)(118.270,0.153)
};
\addlegendentry{CXL/NUMA}
% Paper estimates (from text: ~6 MOPS peak, coro=2 latency ~48us at 144T)
\addplot[color=papercolor,mark=diamond*,thick,dashed] coordinates {
  (1.5,2.0)(3.0,4.0)(5.0,12.0)(6.0,48.0)
};
\addlegendentry{Paper (CX-6, est.)}
% Annotations
\node[font=\scriptsize,anchor=west,numacolor] at (axis cs:120,0.5) {0.15\,$\mu$s};
\node[font=\scriptsize,anchor=south,rdmacolor] at (axis cs:5.0,15) {13.6\,$\mu$s};
\node[font=\scriptsize,anchor=west,papercolor] at (axis cs:6.5,48) {48\,$\mu$s};
\end{axis}
\end{tikzpicture}
\caption{Throughput vs.\ mean latency for YCSB-C (coro=2). Each point represents a different thread count. CXL/NUMA (blue) achieves \textbf{both} higher throughput and lower latency than RDMA and the original paper --- it scales to 118\,MOPS while keeping latency below 0.16\,$\mu$s. RDMA (red) saturates at $\sim$5\,MOPS with latency rising sharply beyond 8 threads. The paper's CX-6 results (green, estimated from reported values) reach $\sim$6\,MOPS with $\sim$48\,$\mu$s latency at 144 threads. This demonstrates CXL's fundamental advantage: eliminating the network stack removes the throughput--latency trade-off inherent in RDMA.}
\label{fig:tput-vs-latency}
\end{figure}

% ──────────────────────────────────────────────────────────────────────────────
\subsection{Scaling Characteristics Summary}
% ──────────────────────────────────────────────────────────────────────────────

In summary, two distinct RDMA bottleneck regimes emerge from our experiments: (1)~\textbf{MN-CPU-bound} (same-rack, $\sim$2\,$\mu$s RTT): throughput plateaus at 4.3--8.3\,MOPS and scales near-linearly with MN thread count; (2)~\textbf{Topology-limited} (multi-rack, $\sim$29\,$\mu$s RTT): throughput plateaus at $\sim$4.5\,MOPS regardless of MN-thread count, coroutine count (C=1--3), or total CN threads, and does not scale. The paper's Fig.~10 result on the same 9-node r320 CX-3 hardware --- reaching $\sim$17\,MOPS with 4 MN threads --- represents a gap we cannot fully explain from our data: our coroutine sweep shows no benefit from C=1--3, and the paper does not disclose its full benchmark configuration. CXL/NUMA belongs to neither RDMA regime: it scales near-linearly to 118\,MOPS at 32 threads, limited only by DRAM bandwidth. See Table~\ref{tab:repro-summary} (\S\ref{sec:repro-ycsb}) and Appendix~\ref{app:tables} for full platform comparisons.

% ══════════════════════════════════════════════════════════════════════════════
\section{Discussion}
% ══════════════════════════════════════════════════════════════════════════════

\subsection{CXL Advantages Over RDMA}

\begin{enumerate}[nosep]
  \item \textbf{Latency:} CXL/NUMA achieves 0.139\,$\mu$s mean latency vs.\ RDMA's 3.04\,$\mu$s --- a \textbf{21.9$\times$} improvement (see Table~\ref{tab:latency-cmp}).
  \item \textbf{Scalability:} Near-linear scaling with thread count (throughput $\propto$ threads) because no shared NIC bottleneck exists.
  \item \textbf{Simplicity:} Eliminating the network stack removes coroutine schedulers, RPC layers, QP management, and memory registration --- reducing code complexity by $\sim$60\%.
  \item \textbf{Memory Efficiency:} No RDMA buffer registration overhead, connection state, or NIC-side memory consumption.
  \item \textbf{Topology Independence:} RDMA throughput is acutely sensitive to network topology: our 9-node multi-rack experiment ($\sim$29\,$\mu$s RTT) capped throughput at $\sim$4.6\,MOPS --- \emph{below} the 3-node same-rack result at 5.04\,MOPS --- despite $2\times$ more CN threads. CXL.mem involves no network fabric, making performance topology-agnostic by construction.
\end{enumerate}

\subsection{CXL Limitations}

\begin{enumerate}[nosep]
  \item \textbf{Single-Machine Scope:} Unlike RDMA (cluster-wide), CXL/NUMA is limited to one machine's socket topology. CXL~3.0 pooling is needed for multi-node.
  \item \textbf{Write Contention:} Without hardware offloading, concurrent writes compete on the memory bus. Software lanes mitigate but don't eliminate this.
  \item \textbf{Resize Coordination:} Shared-memory remap requires atomic generation counters; stale pointers risk segfaults.
  \item \textbf{Persistent Shared Memory:} \texttt{/dev/shm} files require explicit cleanup via signal handlers.
\end{enumerate}

% ══════════════════════════════════════════════════════════════════════════════
\section{Conclusion}
% ══════════════════════════════════════════════════════════════════════════════

This project reproduced and extended Outback from two perspectives: RDMA artifact reproduction on CloudLab Apt \texttt{r320} clusters, and a NUMA-based CXL proxy on a \texttt{c6420} node. These two tracks are distinct: the first validates Outback's published claims; the second explores whether the DMPH design is viable for load/store disaggregated memory.

\textbf{RDMA reproduction.} Using the same Mellanox CX-3 56\,Gbps FDR InfiniBand hardware as the paper, we ran two topologies. On a same-rack 3-node cluster (1\,MN + 2\,CN, $\sim$2\,$\mu$s RTT), we confirmed Outback's core claim: DMPH lookup is MN-CPU-bound under low-RTT conditions, with clear MN-thread scaling (YCSB-C: MT=1 $\to$ 5.04\,MOPS, MT=2 $\to$ 8.27\,MOPS, 1.64$\times$ at 32 total CN threads). The coroutine-depth sweep reproduced the expected hockey-stick curve, with coro=1$\to$2 substantially improving throughput in the unsaturated region and coro=3 yielding diminishing returns near MN-thread saturation. Scaling to the full 9-node topology (1\,MN + 8\,CN, $\sim$29\,$\mu$s multi-rack RTT, 64 total CN threads) revealed a qualitatively different regime: across two independent MN-thread sweeps (Tables~\ref{tab:9node-ycsb-peak},~\ref{tab:9node-mt-scaling}), YCSB-C throughput is essentially flat at 4.54--4.75\,MOPS for MT=1--4 ($\sim$5\% spread is run-to-run variance, not scaling), and our coroutine sweep (C=1/2/3 at 64\,T) showed no benefit from increasing coroutine count --- all counts converge to the same ceiling with latency scaling proportionally. The paper's Fig.~10 linear MN-thread scaling on the same 9-node r320 CX-3 hardware (reaching $\sim$17\,MOPS at 4 MN threads) is plausibly explained by cross-rack CloudLab placement and the resulting $\sim$29\,$\mu$s RTT, but cannot be fully confirmed without the paper's exact node placement, thread pinning, OFED settings, and runtime configuration. The Fig.~12 comparison involves different hardware (r650/CX-6, 288 CN threads) and is not hardware-matched to our experiment. Beyond topology, the reproduction also exposed: write-heavy workloads (YCSB-A, YCSB-F) saturate and degrade at high thread counts; the resize experiment on the separate resize branch exhibits a $\sim$45\% throughput drop with erratic recovery; the actual DMPH index footprint at 20M keys (15.95--16.42\,MB on RDMA, 16.87\,MB on CXL/NUMA at LF=0.95) exceeds the paper's reported 12.5\,MB by 28--35\%, and the RDMA client process RSS reaches 915.8\,MB at 60M keys; and RACE, MICA, and Cluster baselines could not be directly reproduced due to build-breaking issues, so speedup ratios over baselines are not independently verified.

\textbf{CXL/NUMA extension.} Replacing the RDMA transport with POSIX shared memory across NUMA sockets yielded a \textbf{23.5$\times$} throughput gain (118.3\,MOPS at 32 threads vs.\ 5.04\,MOPS on RDMA) and a \textbf{21.9$\times$} latency reduction (0.139\,$\mu$s vs.\ 3.04\,$\mu$s mean) in the NUMA emulation environment. Thread scaling remained near-linear because the NUMA memory bus imposes no NIC bottleneck. The port required re-engineering the transport, removing the coroutine scheduler, building software allocation lanes to replace RDMA queue pairs, and implementing a versioned resize state machine with signal-safe \texttt{/dev/shm} cleanup. However, these results should be interpreted as an \textbf{optimistic upper-bound architectural study} rather than a direct measurement of real CXL hardware. The NUMA proxy eliminates network RTT and MN CPU dispatch overhead but does not model PCIe bandwidth limits, CXL controller latency, CXL switching, or multi-host coherence costs.

\textbf{Broader implications.} The safe conclusion from this work is: we successfully reproduced the main behavior of Outback under RDMA and identified where hardware and topology changes affect performance. The moderate conclusion is: the NUMA-based CXL proxy demonstrates that Outback's DMPH design is promising for load/store disaggregated memory, with read-dominated workloads scaling near-linearly without a network bottleneck. The \emph{unsafe} claim --- that CXL is definitively 20$\times$ faster than RDMA --- is not supported by this work because the hardware, CPU generation, memory capacity, network path, and single-host NUMA setup all differ. What \emph{is} supported is that Outback's DMPH indexing strategy is transport-agnostic: the same index design that enables single-RTT RDMA reads maps directly to single-load CXL accesses. As CXL.mem devices become commercially available, the disaggregated memory architecture Outback targets deserves evaluation on real CXL hardware to determine whether these upper-bound gains survive the PCIe/CXL controller bottleneck.

% ── Limitations ────────────────────────────────────────────────────────────
\subsection{Limitations}\label{sec:conclusion-limitations}

\begin{itemize}[nosep]
  \item \textbf{NUMA as CXL proxy:} Results use inter-socket DDR4 (NUMA), not real CXL hardware. Real CXL latency is typically 200--400\,ns (vs.\ our 130--150\,ns); PCIe bandwidth caps may further limit throughput.

  \item \textbf{Incomplete codebase and reproduction gap:} Broken RACE/MICA/Cluster builds prevent verifying the paper's 5.03$\times$ ratio. Our peak RDMA throughput falls short of the paper's, likely from undisclosed OFED version, hugepage configuration, or DRAM allocation differences.

  \item \textbf{Resize incomplete:} The main upstream resize path is unstable under RDMA load. A separate experimental resize branch allowed limited RDMA resize measurements, but those results should be treated as partial and not a full reproduction of the paper's integrated resize behavior. Our CXL/NUMA resize state machine is independently functional but produces data only for the NUMA transport.

  \item \textbf{Scope:} CXL/NUMA is limited to one physical host; YCSB-E (range scans) cannot be evaluated because DMPH does not support ordered traversal.
\end{itemize}

% ── Future Work ────────────────────────────────────────────────────────────
\subsection{Future Work}

Future work should prioritize: (1)~validating on real CXL hardware (Samsung CMM-D, Intel CXL DIMMs) to determine whether the NUMA upper-bound results survive PCIe bandwidth and 200--400\,ns CXL latency constraints; (2)~direct reproduction of the RACE, MICA, and Cluster baselines to independently verify speedup ratios; (3)~a stable, integrated resize implementation that preserves service continuity during hash-table expansion; (4)~improved write-heavy workload support via per-lane write buffers and \texttt{CLWB}/\texttt{CLFLUSHOPT} on CXL; and (5)~evaluation of an alternative ordered index or hybrid design to support range scans (YCSB-E), which the DMPH architecture cannot inherently provide.

% ══════════════════════════════════════════════════════════════════════════════
\appendices
\section{Hardware Specifications}\label{app:hw}
% ══════════════════════════════════════════════════════════════════════════════

\begin{table}[H]
\centering
\caption{Hardware comparison}
\label{tab:hw}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Component} & \textbf{r320 (RDMA)} & \textbf{c6420 (CXL/NUMA)} \\
\midrule
CPU & Xeon E5-2450, 8C/16T, 2.1\,GHz, 20\,MB L3 & 2$\times$ Xeon Gold 6142, 16C/32T, 2.6\,GHz \\
Memory & 16\,GB DDR3-1600 (4$\times$4\,GB RDIMMs) & 384\,GB DDR4 \\
Network & Mellanox MX354A ConnectX-3, 56\,Gbps FDR IB & N/A (intra-node) \\
NUMA Nodes & 1 & 2 \\
Nodes Used & 3 (1MN + 2CN) & 1 (NUMA0=CN, NUMA1=MN) \\
\bottomrule
\end{tabular}}
\end{table}

\section{Modified Source Files}

\begin{table}[H]
\centering
\caption{Files created/modified for the CXL/NUMA port}
\label{tab:files}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lp{5cm}@{}}
\toprule
\textbf{File} & \textbf{Purpose} \\
\midrule
\texttt{xutils/numa\_memory.hh} & NUMA-aware region allocator (replaces HugeRegion) \\
\texttt{xcomm/.../numa\_transport.hh} & Shared-memory transport: registry, epochs, resize FSM \\
\texttt{outback/trait\_numa.hpp} & NUMA-specific type definitions \\
\texttt{outback/outback\_server\_numa.hh} & Server direct-memory operations \\
\texttt{outback/outback\_client\_numa.hh} & Client shared-memory access \& version tracking \\
\texttt{benchs/outback/server\_numa.cc} & Server benchmark harness \\
\texttt{benchs/outback/client\_numa.cc} & Client benchmark with histogram telemetry \\
\texttt{build\_numa.sh} & Build script for NUMA targets \\
\bottomrule
\end{tabular}}
\end{table}

\section{Key Commands}

\textbf{RDMA:}
\begin{lstlisting}[language=bash,basicstyle=\ttfamily\scriptsize]
# Server (MN)
sudo taskset -c 0 ./build/benchs/outback/server \
  --seconds=200 --nkeys=50000000 \
  --mem_threads=1 --workloads=ycsbc \
  --nic_idx=0

# Client (CN)
sudo taskset -c 0-$((threads-1)) \
  ./build/benchs/outback/client \
  --nic_idx=0 \
  --server_addr=192.168.1.2:8888 \
  --threads=$threads --coros=2 \
  --seconds=120 --nkeys=50000000 \
  --bench_nkeys=10000000 \
  --workloads=ycsbc
\end{lstlisting}

\textbf{CXL/NUMA:}
\begin{lstlisting}[language=bash,basicstyle=\ttfamily\scriptsize]
# Server (MN - NUMA Node 1)
sudo numactl --physcpubind=0 \
  --membind=1 \
  ./build/benchs/outback/server_numa \
  --numa_node=1 --nkeys=50000000 \
  --seconds=120 --mem_threads=1 \
  --workloads=ycsbc

# Client (CN - NUMA Node 0)
sudo numactl \
  --physcpubind=2-$((threads+1)) \
  --membind=0 \
  ./build/benchs/outback/client_numa \
  --nkeys=50000000 \
  --bench_nkeys=10000000 \
  --threads=$threads --seconds=120 \
  --mem_threads=1 --coros=2 \
  --workloads=ycsbc
\end{lstlisting}

% ══════════════════════════════════════════════════════════════════════════════
\section{Detailed Numerical Results}\label{app:tables}
% ══════════════════════════════════════════════════════════════════════════════

\subsection*{RDMA YCSB Raw Measurements}

\begin{table}[H]
\caption{RDMA YCSB-C throughput and latency (coro=2, mem\_threads=1)}
\label{tab:rdma-ycsbc}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.724 & 2.06 \\
2  & 1MN 1CN diff CPU    & 1.411 & 2.11 \\
4  & 1MN 1CN diff CPU    & 2.770 & 2.15 \\
8  & 1MN 1CN diff CPU    & 4.503 & 3.04 \\
16 & 1MN 1CN diff CPU    & 4.325 & 6.69 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.802 & 2.18 \\
8  & 1MN 2CN diff CPU    & 4.269 & 3.09 \\
16 & 1MN 2CN diff CPU    & 4.833 & 6.75 \\
32 & 1MN 2CN diff CPU    & 5.040 & 13.63 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-B throughput and latency (coro=2, mem\_threads=1)}
\label{tab:rdma-ycsbb}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.731 & 2.06 \\
2  & 1MN 1CN diff CPU    & 1.451 & 2.09 \\
4  & 1MN 1CN diff CPU    & 2.836 & 2.14 \\
8  & 1MN 1CN diff CPU    & 3.722 & 4.47 \\
16 & 1MN 1CN diff CPU    & 4.091 & 8.16 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.777 & 2.23 \\
8  & 1MN 2CN diff CPU    & 4.043 & 3.50 \\
16 & 1MN 2CN diff CPU    & 4.461 & 6.91 \\
32 & 1MN 2CN diff CPU    & 4.439 & 15.24 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-A throughput and latency (coro=2, mem\_threads=1)}
\label{tab:rdma-ycsba}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.740 & 2.07 \\
2  & 1MN 1CN diff CPU    & 1.471 & 2.10 \\
4  & 1MN 1CN diff CPU    & 2.746 & 2.22 \\
8  & 1MN 1CN diff CPU    & 3.632 & 3.90 \\
16 & 1MN 1CN diff CPU    & 3.783 & 7.99 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.709 & 2.23 \\
8  & 1MN 2CN diff CPU    & 3.649 & 4.06 \\
16 & 1MN 2CN diff CPU    & 3.873 & 8.34 \\
32 & 1MN 2CN diff CPU    & 4.049 & 16.27 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-D throughput and latency (coro=2, mem\_threads=1)}
\label{tab:rdma-ycsbd}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.744 & 2.11 \\
2  & 1MN 1CN diff CPU    & 1.460 & 2.17 \\
4  & 1MN 1CN diff CPU    & 2.699 & 2.34 \\
8  & 1MN 1CN diff CPU    & 3.832 & 3.57 \\
16 & 1MN 1CN diff CPU    & 3.900 & 7.47 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.720 & 2.34 \\
8  & 1MN 2CN diff CPU    & 3.982 & 2.27 \\
16 & 1MN 2CN diff CPU    & 4.229 & 7.80 \\
32 & 1MN 2CN diff CPU    & 4.281 & 15.66 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-F throughput and latency (coro=2, mem\_threads=1)}
\label{tab:rdma-ycsbf}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.626 & 2.43 \\
2  & 1MN 1CN diff CPU    & 1.194 & 2.60 \\
4  & 1MN 1CN diff CPU    & 1.939 & 3.43 \\
8  & 1MN 1CN diff CPU    & 2.213 & 6.55 \\
16 & 1MN 1CN diff CPU    & 2.370 & 12.68 \\
\midrule
4  & 1MN 2CN diff CPU    & 1.926 & 3.46 \\
8  & 1MN 2CN diff CPU    & 2.157 & 6.70 \\
16 & 1MN 2CN diff CPU    & 2.501 & 12.08 \\
32 & 1MN 2CN diff CPU    & 2.354 & 26.25 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{RDMA vs.\ Paper Comparison Tables}

\begin{table}[H]
\centering
\caption{Paper Figure~9 peak throughput vs.\ our RDMA reproduction (per shard, MOPS)}
\label{tab:paper-fig9}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrl@{}}
\toprule
\textbf{Workload} & \textbf{Paper Outback (CX-6)} & \textbf{Paper Threads} & \textbf{RDMA 32T 2CN} & \textbf{vs Paper} \\
\midrule
YCSB-A (50\%U) & 5.50 & 144 & 4.049 & 0.74$\times$ \\
YCSB-B (5\%U)  & 5.82 & 144 & 4.439 & 0.76$\times$ \\
YCSB-C (100\%R) & 6.01 & 72--144 & 5.040 & 0.84$\times$ \\
YCSB-D (5\%I)   & $\sim$5.9 & 144 & 4.281 & 0.73$\times$ \\
YCSB-F (25\%I/25\%U) & 3.62 & 144 & 2.354 & 0.65$\times$ \\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]
\centering
\caption{Paper Fig.~10 vs.\ RDMA per-MN-thread peak throughput (MOPS). Exact hardware match (r320/CX-3 IB FDR), normalized to per-MN-thread.}
\label{tab:paper-fig10}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrrl@{}}
\toprule
\textbf{Workload} & \textbf{Fig.10 Agg.} & \textbf{Fig.10 /MN} & \textbf{Ours (32T)} & \textbf{Ours /MN} & \textbf{Ratio} \\
 & \textbf{(4MN, 64T)} & \textbf{(est.)} & \textbf{(1MN, 2CN)} & & \\
\midrule
YCSB-A & $\sim$15.0 & $\sim$3.75 & 4.049 & 4.049 & 1.08$\times$ ours \\
YCSB-B & $\sim$16.5 & $\sim$4.13 & 4.439 & 4.439 & 1.08$\times$ ours \\
YCSB-C & $\sim$17.0 & $\sim$4.25 & 5.040 & 5.040 & 1.19$\times$ ours \\
YCSB-D & $\sim$16.0 & $\sim$4.00 & 4.281 & 4.281 & 1.07$\times$ ours \\
YCSB-F & $\sim$9.0 & $\sim$2.25 & 2.354 & 2.354 & 1.05$\times$ ours \\
\bottomrule
\end{tabular}}
\end{table}

\subsection*{RDMA Coroutine and MN Thread Scaling}

\begin{table}[H]
\centering
\caption{RDMA YCSB-C coroutine effect (1MN 1CN, threads on different CPUs)}
\label{tab:rdma-coro-1cn}
\scriptsize
\begin{tabular}{@{}rrrr|rrr@{}}
\toprule
& \multicolumn{3}{c|}{\textbf{Throughput (MOPS)}} & \multicolumn{3}{c}{\textbf{Mean Latency ($\mu$s)}} \\
\textbf{Threads} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} \\
\midrule
1  & 0.366 & 0.724 & 1.081 & 2.05 & 2.06 & 2.07 \\
2  & 0.706 & 1.411 & 2.081 & 2.12 & 2.11 & 2.16 \\
4  & 1.385 & 2.770 & 3.680 & 2.19 & 2.15 & 2.78 \\
8  & 2.788 & 4.503 & 4.748 & 2.14 & 3.04 & 4.44 \\
16 & 4.375 & 4.325 & 4.402 & 3.16 & 6.69 & 10.26 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-C coroutine effect (1MN 2CN)}
\label{tab:rdma-coro-2cn}
\scriptsize
\begin{tabular}{@{}rrrr|rrr@{}}
\toprule
& \multicolumn{3}{c|}{\textbf{Throughput (MOPS)}} & \multicolumn{3}{c}{\textbf{Mean Latency ($\mu$s)}} \\
\textbf{Threads} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} \\
\midrule
4  & 1.409 & 2.802 & 3.238 & 2.12 & 2.18 & 3.08 \\
8  & 2.808 & 4.269 & 4.196 & 2.09 & 3.09 & 5.10 \\
16 & 4.443 & 4.833 & 4.224 & 2.18 & 6.75 & 10.85 \\
32 & 4.870 & 5.040 & 4.414 & 6.01 & 13.63 & 21.18 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-C: mem\_threads scaling (1MN 2CN, coro=2)}
\label{tab:rdma-memthreads}
\scriptsize
\begin{tabular}{@{}rrrr|rrr@{}}
\toprule
& \multicolumn{3}{c|}{\textbf{Throughput (MOPS)}} & \multicolumn{3}{c}{\textbf{Mean Latency ($\mu$s)}} \\
\textbf{Threads} & \textbf{MT=1} & \textbf{MT=2} & \textbf{MT=3} & \textbf{MT=1} & \textbf{MT=2} & \textbf{MT=3} \\
\midrule
1  & 0.724  & 0.725  & ---    & 2.06  & 2.07  & --- \\
4  & 2.770  & 2.790  & ---    & 2.15  & 2.18  & --- \\
8  & 4.503  & 5.188  & ---    & 3.04  & 2.39  & --- \\
16 & 4.325  & 6.761  & ---    & 6.69  & 4.94  & --- \\
32 (2CN) & 5.040 & 8.266 & --- & 13.63 & 8.04 & --- \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA YCSB-C with mem\_threads=2: coroutine effect (1MN 2CN)}
\label{tab:rdma-mt2-coro}
\scriptsize
\begin{tabular}{@{}rrrr|rrr@{}}
\toprule
& \multicolumn{3}{c|}{\textbf{Throughput (MOPS)}} & \multicolumn{3}{c}{\textbf{Mean Latency ($\mu$s)}} \\
\textbf{Threads} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} \\
\midrule
4  & 1.423 & 2.823 & 4.044 & 2.12 & 2.14 & 2.18 \\
8  & 2.791 & 5.390 & 6.802 & 2.17 & 2.27 & 3.07 \\
16 & 5.436 & 8.333 & 7.933 & 2.32 & 3.15 & 6.12 \\
32 & 7.772 & 8.266 & 8.449 & 3.95 & 8.04 & 12.26 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{RDMA 9-Node Full-Scale Experiments}

\begin{table}[H]
\centering
\caption{9-node YCSB peak throughput (MOPS) at 64 total threads (8\,CN $\times$ 8\,T/CN, coro=2, 50M keys). Throughput is client-limited due to $\sim$29\,$\mu$s multi-rack RTT; no MN-thread scaling is visible.}
\label{tab:9node-ycsb-peak}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textbf{Workload} & \textbf{MT=1} & \textbf{MT=2} & \textbf{MT=3} & \textbf{MT=4} \\
\midrule
YCSB-C & 4.655 & 4.752 & 4.571 & 4.614 \\
YCSB-B & 3.914 & 4.181 & 3.646 & 3.691 \\
YCSB-A & 3.783 & 3.531 & 3.612 & 3.612 \\
YCSB-D & 4.073 & 3.982 & 3.838 & 3.823 \\
YCSB-F & 2.530 & 2.510 & 2.451 & 2.444 \\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]
\centering
\caption{9-node MN-thread scaling: YCSB-C, 64 total threads (8\,CN $\times$ 8\,T/CN), coro=2. Throughput is flat (no MN scaling) because the client is the bottleneck at $\sim$29\,$\mu$s multi-rack RTT.}
\label{tab:9node-mt-scaling}
\scriptsize
\begin{tabular}{@{}rrr@{}}
\toprule
\textbf{MN Threads} & \textbf{Tput (MOPS)} & \textbf{Mean Latency ($\mu$s)} \\
\midrule
1 & 4.681 & 28.885 \\
2 & 4.537 & 28.939 \\
3 & 4.638 & 29.041 \\
4 & 4.573 & 29.332 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{9-node coroutine sweep (YCSB-C): throughput (MOPS)\,/\,mean latency ($\mu$s) at MT=1 and MT=2. ``Total T'' = total CN threads across 8 CNs. All coroutine counts converge to the same $\sim$4.5\,MOPS ceiling at 64\,T, confirming client-side bottleneck.}
\label{tab:9node-coro}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}r rrr|rrr@{}}
\toprule
 & \multicolumn{3}{c|}{\textbf{MT=1: Tput\,/\,Lat}} & \multicolumn{3}{c}{\textbf{MT=2: Tput\,/\,Lat}} \\
\textbf{Total T} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} & \textbf{C=1} & \textbf{C=2} & \textbf{C=3} \\
\midrule
 8 & 2.261\,/\,3.0  & 2.427\,/\,6.1  & 2.539\,/\,9.1  & 2.453\,/\,2.9  & 2.504\,/\,5.9  & 2.574\,/\,9.0  \\
16 & 3.341\,/\,4.1  & 3.433\,/\,9.0  & 3.630\,/\,13.1 & 3.327\,/\,4.2  & 3.381\,/\,9.2  & 3.597\,/\,13.5 \\
32 & 4.246\,/\,7.2  & 4.254\,/\,15.2 & 4.257\,/\,23.3 & 4.029\,/\,7.5  & 4.103\,/\,15.8 & 4.039\,/\,23.7 \\
64 & 4.735\,/\,13.7 & 4.417\,/\,29.1 & 4.714\,/\,43.1 & 4.594\,/\,14.0 & 4.613\,/\,28.8 & 4.450\,/\,44.9 \\
\bottomrule
\end{tabular}}
\end{table}

\subsection*{RDMA Dataset and Memory Measurements}

\begin{table}[H]
\centering
\caption{RDMA: FB dataset, uniform, coro=2, mem\_threads=1}
\label{tab:rdma-fb}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.731 & 2.05 \\
2  & 1MN 1CN diff CPU    & 1.418 & 2.11 \\
4  & 1MN 1CN diff CPU    & 2.773 & 2.15 \\
8  & 1MN 1CN diff CPU    & 4.541 & 3.04 \\
16 & 1MN 1CN diff CPU    & 4.679 & 6.48 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.737 & 2.14 \\
8  & 1MN 2CN diff CPU    & 4.085 & 3.21 \\
16 & 1MN 2CN diff CPU    & 4.620 & 6.65 \\
32 & 1MN 2CN diff CPU    & 4.821 & 13.68 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA: OSM dataset, uniform, coro=2, mem\_threads=1}
\label{tab:rdma-osm}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Threads} & \textbf{Config} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} \\
\midrule
1  & 1MN 1CN             & 0.730 & 2.06 \\
2  & 1MN 1CN diff CPU    & 1.405 & 2.12 \\
4  & 1MN 1CN diff CPU    & 2.803 & 2.13 \\
8  & 1MN 1CN diff CPU    & 4.514 & 3.04 \\
16 & 1MN 1CN diff CPU    & 4.436 & 6.74 \\
\midrule
4  & 1MN 2CN diff CPU    & 2.745 & 2.17 \\
8  & 1MN 2CN diff CPU    & 4.104 & 3.21 \\
16 & 1MN 2CN diff CPU    & 4.741 & 6.20 \\
32 & 1MN 2CN diff CPU    & 4.807 & 12.67 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA dataset: mem\_threads scaling and KV count effects (1MN 2CN, 32T)}
\label{tab:rdma-dataset-extra}
\scriptsize
\begin{tabular}{@{}llrr@{}}
\toprule
\textbf{Config} & \textbf{Setting} & \textbf{FB (MOPS)} & \textbf{OSM (MOPS)} \\
\midrule
mem\_threads=1  & 50M keys & 4.821 & 4.807 \\
mem\_threads=2  & 50M keys & 7.918 & 8.117 \\
mem\_threads=3  & 50M keys & 10.844 & 10.588 \\
\midrule
KV=20M & mem\_threads=1  & 4.491 & 4.676 \\
KV=80M & mem\_threads=1  & \multicolumn{2}{c}{OOM on server side} \\
\midrule
LF=0.75 & 50M keys & 4.504 & 4.341 \\
LF=0.85 & 50M keys & 4.400 & 4.393 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA: DMPH index size (MB) by KV count and load factor}
\label{tab:rdma-dmph}
\scriptsize
\begin{tabular}{@{}rrrrr@{}}
\toprule
\textbf{NKeys} & \textbf{LF=0.80} & \textbf{LF=0.85} & \textbf{LF=0.90} & \textbf{LF=0.95} \\
\midrule
20M  & 15.48 & 15.95 & 16.42 & 16.42 \\
40M  & 30.95 & 31.88 & 32.82 & 32.82 \\
60M  & 61.88 & 63.75 & 32.82 & 32.82 \\
80M  & 61.88 & 63.75 & 65.62 & 65.62 \\
100M & 61.88 & 63.75 & 65.62 & 65.62 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{RDMA: client process RSS (MB) by KV count and load factor (OSM dataset)}
\label{tab:rdma-rss}
\scriptsize
\begin{tabular}{@{}rrr@{}}
\toprule
\textbf{NKeys} & \textbf{LF=0.80 (MB)} & \textbf{LF=0.85 (MB)} \\
\midrule
20M  & 380.8 & 364.6 \\
40M  & 563.9 & 573.5 \\
50M  & 640.3 & 649.4 \\
60M  & 896.9 & 915.8 \\
\bottomrule
\end{tabular}
\end{table}

\subsection*{CXL/NUMA Raw Measurements}

\begin{table}[H]
\centering
\caption{CXL/NUMA YCSB-C throughput and latency (coro=2, mem\_threads=1)}
\label{tab:numa-ycsbc}
\scriptsize
\begin{tabular}{@{}rrrrr@{}}
\toprule
\textbf{Threads} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} & \textbf{P99 ($\mu$s)} & \textbf{P999 ($\mu$s)} \\
\midrule
1  & 4.794  & 0.126 & 0.40 & 0.50 \\
2  & 9.056  & 0.135 & 0.40 & 0.50 \\
4  & 17.833 & 0.137 & 0.40 & 0.60 \\
8  & 35.737 & 0.139 & 0.50 & 0.60 \\
16 & 70.091 & 0.141 & 0.50 & 0.70 \\
32 & 118.270 & 0.153 & 0.50 & 0.70 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{CXL/NUMA YCSB-C: coroutine/batch effect}
\label{tab:numa-coro}
\scriptsize
\begin{tabular}{@{}rrrr|rrr@{}}
\toprule
& \multicolumn{3}{c|}{\textbf{Throughput (MOPS)}} & \multicolumn{3}{c}{\textbf{Mean Latency ($\mu$s)}} \\
\textbf{Threads} & \textbf{Batch=1} & \textbf{Batch=2} & \textbf{Batch=3} & \textbf{Batch=1} & \textbf{Batch=2} & \textbf{Batch=3} \\
\midrule
1  & 4.776  & 4.794  & 4.743  & 0.126 & 0.126 & 0.126 \\
4  & 17.734 & 17.833 & 17.675 & 0.138 & 0.137 & 0.137 \\
8  & 35.827 & 35.737 & 35.399 & 0.138 & 0.139 & 0.138 \\
16 & 70.214 & 70.091 & 69.548 & 0.140 & 0.141 & 0.140 \\
32 & 116.106 & 118.270 & 121.286 & 0.155 & 0.153 & 0.152 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[H]
\centering
\caption{CXL/NUMA results across YCSB workloads (coro=2, mem\_threads=1)}
\label{tab:numa-ycsb-all}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}llrrr@{}}
\toprule
\textbf{Workload} & \textbf{Threads} & \textbf{Tput (MOPS)} & \textbf{Mean Lat ($\mu$s)} & \textbf{P99 ($\mu$s)} \\
\midrule
\multirow{4}{*}{YCSB-B (95R/5U)} & 4  & 17.775 & 0.142 & 0.60 \\
  & 8  & 35.772 & 0.141 & 0.60 \\
  & 16 & 69.087 & 0.144 & 0.50 \\
  & 32 & 122.821 & 0.141 & 0.50 \\
\midrule
\multirow{4}{*}{YCSB-A (50R/50U)} & 4  & 10.422 & 0.295 & 1.00 \\
  & 8  & 21.909 & 0.274 & 1.30 \\
  & 16 & 44.183 & 0.275 & 1.90 \\
  & 32 & 85.514 & 0.263 & 2.80 \\
\midrule
\multirow{4}{*}{YCSB-D (95R/5Ins)} & 4  & 19.691 & 0.094 & 0.60 \\
  & 8  & 40.854 & 0.089 & 0.50 \\
  & 16 & 82.002 & 0.088 & 0.50 \\
  & 32 & 129.707 & 0.087 & 0.70 \\
\midrule
\multirow{4}{*}{YCSB-F (50R/25I/25U)} & 4  & 8.460 & 0.276 & 0.80 \\
  & 8  & 18.189 & 0.243 & 0.70 \\
  & 16 & 31.935 & 0.269 & 0.80 \\
  & 32 & 46.775 & 0.315 & 0.90 \\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}[H]
\centering
\caption{CXL/NUMA: Facebook (FB) and OpenStreetMap (OSM) datasets (uniform, coro=2)}
\label{tab:numa-datasets}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textbf{Config (32T)} & \textbf{FB (MOPS)} & \textbf{FB Lat} & \textbf{OSM (MOPS)} & \textbf{OSM Lat} \\
\midrule
mem\_threads=1 & 118.108 & 0.154 & 118.017 & 0.153 \\
mem\_threads=2 & 119.454 & 0.153 & 120.604 & 0.153 \\
mem\_threads=3 & 118.380 & 0.153 & 118.392 & 0.154 \\
\midrule
KV=20M & 149.266 & 0.108 & 150.242 & 0.107 \\
KV=50M & 118.108 & 0.154 & 118.017 & 0.153 \\
KV=80M & 100.621 & 0.199 & 101.690 & 0.200 \\
\midrule
LF=0.75 & 124.817 & 0.141 & 124.982 & 0.140 \\
LF=0.85 & 121.532 & 0.146 & 121.216 & 0.147 \\
LF=0.95 & 118.108 & 0.154 & 118.017 & 0.153 \\
\bottomrule
\end{tabular}}
\end{table}

\subsection*{Three-Way Comparison Tables}

\begin{table}[H]
\centering
\caption{Three-way YCSB-C throughput comparison (MOPS per shard)}
\label{tab:three-way}
\scriptsize
\begin{tabular}{@{}rrrr@{}}
\toprule
\textbf{Threads} & \textbf{Paper CX-6 (r650)} & \textbf{RDMA (r320)} & \textbf{CXL/NUMA (c6420)} \\
\midrule
1  & --- & 0.724 & 4.794 \\
2  & --- & 1.411 & 9.056 \\
4  & --- & 2.770 & 17.833 \\
8  & $\sim$1.2$^*$ & 4.503 & 35.737 \\
16 & --- & 4.325 & 70.091 \\
32 & --- & 5.040 (2CN) & 118.270 \\
72 & 6.01 & --- & --- \\
144 & 6.01 & --- & --- \\
\bottomrule
\end{tabular}

\vspace{2pt}
{\scriptsize $^*$Estimated from Figure~9c curve shape; paper only states peak=6.01 at 72T.}
\end{table}

\begin{table}[H]
\centering
\caption{Paper Figure~11 dataset results vs.\ CXL/NUMA (MOPS, Get throughput)}
\label{tab:paper-fig11}
\scriptsize
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lrrrrr@{}}
\toprule
\textbf{Dataset} & \textbf{Paper Outback} & \textbf{Paper RACE} & \textbf{Paper MICA} & \textbf{Paper Cluster} & \textbf{CXL/NUMA} \\
 & \textbf{(CX-6, 144T)} & & & & \textbf{(32T)} \\
\midrule
FB, uniform & $\sim$6.0 & $\sim$4.35$^\dagger$ & $\sim$2.96$^\dagger$ & $\sim$5.45$^\dagger$ & \textbf{118.11} \\
OSM, uniform & $\sim$6.0 & $\sim$4.35$^\dagger$ & $\sim$2.96$^\dagger$ & $\sim$5.31$^\dagger$ & \textbf{118.02} \\
FB, zipfian & $\sim$6.0 & $\sim$4.44$^\ddagger$ & $\sim$2.93$^\ddagger$ & $\sim$5.31$^\ddagger$ & --- \\
OSM, zipfian & $\sim$6.0 & $\sim$4.35$^\dagger$ & --- & --- & --- \\
\bottomrule
\end{tabular}}

\vspace{2pt}
{\scriptsize $^\dagger$Derived from 1.38$\times$/2.03$\times$/1.1$\times$ at 144T (uniform FB). \quad $^\ddagger$Derived from 1.35$\times$/2.05$\times$/1.13$\times$ at 144T (zipfian FB).}
\end{table}

\begin{table*}[t]
\centering
\caption{Paper Figure~16 vs.\ RDMA and CXL/NUMA measured DMPH index size (MB). Paper formula: $(2.33 + 2/\epsilon) \times n$ bits; paper states ``around 12.5\,MB'' at 20M and ``below 60\,MB'' at 100M.}
\label{tab:fig16-cmp}
\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}r rrrr rrrr@{}}
\toprule
 & \multicolumn{4}{c}{\textbf{LF = 0.80}} & \multicolumn{4}{c}{\textbf{LF = 0.85}} \\
\cmidrule(lr){2-5}\cmidrule(lr){6-9}
\textbf{NKeys} & Theory & Paper$^\dagger$ & RDMA & CXL & Theory & Paper$^\dagger$ & RDMA & CXL \\
\midrule
20M  & 11.52 & $\sim$12.5 & 15.48 & 15.47 & 11.17 & $\sim$12.5 & 15.95 & 15.93 \\
40M  & 23.03 & $\sim$25 & 30.95 & 30.93 & 22.33 & $\sim$25 & 31.88 & 31.87 \\
60M  & 34.55 & $\sim$37 & \textbf{61.88} & \textbf{61.87} & 33.50 & $\sim$37 & \textbf{63.75} & \textbf{63.73} \\
80M  & 46.06 & $\sim$50 & 61.88 & 61.87 & 44.66 & $\sim$50 & 63.75 & 63.73 \\
100M & 57.58 & $<$60 & 61.88 & 61.87 & 55.83 & $<$60 & 63.75 & 63.73 \\
\midrule
 & \multicolumn{4}{c}{\textbf{LF = 0.90}} & \multicolumn{4}{c}{\textbf{LF = 0.95}} \\
\cmidrule(lr){2-5}\cmidrule(lr){6-9}
\textbf{NKeys} & Theory & Paper$^\dagger$ & RDMA & CXL & Theory & Paper$^\dagger$ & RDMA & CXL \\
\midrule
20M  & 10.85 & $\sim$12.5 & 16.42 & 16.40 & 10.57 & $\sim$12.5 & 16.42 & \textbf{16.87} \\
40M  & 21.71 & $\sim$25 & 32.82 & 32.80 & 21.15 & $\sim$25 & 32.82 & \textbf{33.73} \\
60M  & 32.56 & $\sim$37 & 32.82 & 32.80 & 31.72 & $\sim$37 & 32.82 & \textbf{33.73} \\
80M  & 43.41 & $\sim$50 & 65.62 & 65.60 & 42.30 & $\sim$50 & 65.62 & \textbf{67.47} \\
100M & 54.27 & $<$60 & 65.62 & 65.60 & 52.87 & $<$60 & 65.62 & \textbf{67.47} \\
\bottomrule
\end{tabular}%
}

\vspace{2pt}
{\scriptsize $^\dagger$Estimated from paper's stated anchors. Bold CXL values at LF=0.95 differ from RDMA due to slightly larger Othello arrays.}
\end{table*}

% ══════════════════════════════════════════════════════════════════════════════
\begin{thebibliography}{99}
% ══════════════════════════════════════════════════════════════════════════════

\bibitem{outback}
Y.~Liu, M.~Xie, S.~Shi, Y.~Xu, H.~Litz, and C.~Qian,
``Outback: Fast and Communication-efficient Index for Key-Value Store on
  Disaggregated Memory,''
\emph{Proc.\ VLDB Endow.}, vol.~18, no.~2, pp.~335--348, 2024.
DOI:~\href{https://doi.org/10.14778/3705829.3705849}{10.14778/3705829.3705849}.
(arXiv preprint arXiv:2502.08982.)

\bibitem{race}
P.~Zuo, J.~Sun, L.~Yang, S.~Zhang, and Y.~Hua,
``One-Sided {RDMA}-Conscious Extendible Hashing for Disaggregated Memory,''
in \emph{Proc.\ USENIX Annual Technical Conference (ATC)}, 2021, pp.~15--29.

\bibitem{mica}
H.~Lim, D.~Han, D.~G.~Andersen, and M.~Kaminsky,
``{MICA}: A Holistic Approach to Fast In-Memory Key-Value Storage,''
in \emph{Proc.\ 11th USENIX Symposium on Networked Systems Design and
  Implementation (NSDI)}, 2014, pp.~239--255.

\bibitem{fasst}
A.~Kalia, M.~Kaminsky, and D.~G.~Andersen,
``{FaSST}: Fast, Scalable and Simple Distributed Transactions with
  Two-Sided {(RDMA)} Datagram {RPCs},''
in \emph{Proc.\ 12th USENIX Symposium on Operating Systems Design and
  Implementation (OSDI)}, 2016, pp.~185--201.

\bibitem{drtmr}
X.~Wei, J.~Shi, Y.~Chen, R.~Chen, and H.~Chen,
``Fast In-Memory Transaction Processing Using {RDMA} and {HTM},''
in \emph{Proc.\ 25th ACM Symposium on Operating Systems Principles (SOSP)},
  2015, pp.~87--104.
DOI:~\href{https://doi.org/10.1145/2815400.2815419}{10.1145/2815400.2815419}.

\bibitem{drtmh}
X.~Wei, Z.~Dong, R.~Chen, and H.~Chen,
``Deconstructing {RDMA}-enabled Distributed Transactions: Hybrid is Better!''
in \emph{Proc.\ 13th USENIX Symposium on Operating Systems Design and
  Implementation (OSDI)}, 2018, pp.~233--251.

\bibitem{rolex}
P.~Li, Y.~Hua, P.~Zuo, Z.~Chen, and J.~Sheng,
``{ROLEX}: A Scalable {RDMA}-oriented Learned Key-Value Store for
  Disaggregated Memory Systems,''
in \emph{Proc.\ 21st USENIX Conference on File and Storage Technologies
  (FAST)}, 2023, pp.~99--114.

\bibitem{ludo}
S.~Shi and C.~Qian,
``Ludo Hashing: Compact, Fast, and Dynamic Key-Value Lookups for
  Practical Network Systems,''
\emph{Proc.\ ACM Meas.\ Anal.\ Comput.\ Syst.\ (SIGMETRICS)}, vol.~4, no.~2,
  article 34, 2020.
DOI:~\href{https://doi.org/10.1145/3392140}{10.1145/3392140}.

\bibitem{ycsb}
B.~F.~Cooper, A.~Silberstein, E.~Tam, R.~Ramakrishnan, and R.~Sears,
``Benchmarking Cloud Serving Systems with {YCSB},''
in \emph{Proc.\ 1st ACM Symposium on Cloud Computing (SoCC)}, 2010,
  pp.~143--154.
DOI:~\href{https://doi.org/10.1145/1807128.1807152}{10.1145/1807128.1807152}.

\bibitem{cxl}
{CXL Consortium},
``Compute Express Link Specification, Revision 3.0,''
\emph{CXL Consortium White Paper}, 2022.
Available: \url{https://www.computeexpresslink.org/}.

\bibitem{chash}
H.~Li, D.~Zhang, Y.~Hua, P.~Zuo, and J.~Sheng,
``{CHash}: Enabling Efficient Persistent Hashing on {CXL}-Attached Memory,''
in \emph{Proc.\ 23rd USENIX Conference on File and Storage Technologies
  (FAST)}, 2025.

\bibitem{mind2021}
J.~Le, H.~Lee, Y.~Kwon, S.~Kannan, and P.~Gibbons,
``{MIND}: In-Network Memory Management for Disaggregated Data Centers,''
in \emph{Proc.\ 28th ACM Symposium on Operating Systems Principles (SOSP)},
  2021, pp.~488--504.
DOI:~\href{https://doi.org/10.1145/3477132.3483561}{10.1145/3477132.3483561}.

\bibitem{aifm2020}
Z.~Ruan, M.~Schwarzkopf, M.~Aguilera, and A.~Belay,
``{AIFM}: High-Performance, Application-Integrated Far Memory,''
in \emph{Proc.\ 14th USENIX Symposium on Operating Systems Design and
  Implementation (OSDI)}, 2020, pp.~315--332.

\bibitem{carbink2022}
Y.~Zhou, H.~Wassel, S.~Liu, J.~Gao, J.~Mickens, M.~Yu, C.~Jamieson,
  H.~Madhyastha, and V.~Chandra,
``Carbink: Fault-Tolerant Far Memory,''
in \emph{Proc.\ 16th USENIX Symposium on Operating Systems Design and
  Implementation (OSDI)}, 2022, pp.~55--71.

\end{thebibliography}

% ══════════════════════════════════════════════════════════════════════════════

\end{document}
